### 2022-03-18 script/paper 3.Rmd
Add files via upload

---
title: "Untitled"
author: "Jiayi Du"
date: "2022/3/17"
output: pdf_document
---

```{r}
gss<-read.csv("gss.csv",header=TRUE)
gss<-gss%>%select(age,feelings_life,sex,marital_status,education,hh_size,average_hours_worked,income_family,income_respondent)
```

```{r}
gss<-gss%>%na.omit(gss)
gss<-gss%>%filter(marital_status=="Married"|marital_status=="Single, never married")%>%filter(average_hours_worked!="Don't know")

```

```{r}
library(ggplot2)
ggplot(gss,aes(x=feelings_life,fill=income_family))+geom_histogram(position = position_dodge(0.75),binwidth = 1)+facet_grid(.~marital_status)
ggplot(gss,aes(x=feelings_life,fill=average_hours_worked))+geom_histogram(position = position_dodge(0.75),binwidth = 1)+facet_grid(.~marital_status)

```

```{r}
ggplot(aes(x = age, fill = marital_status), data = gss) +geom_histogram(binwidth = 0.2)+facet_wrap(~feelings_life)
ggplot(aes(x = feelings_life, fill = sex), data = gss) +geom_bar(position = "dodge")+facet_wrap(~marital_status)
```

```{r}

```

### 2022-03-18 output/paper 3.Rmd
first

--- 2022-03-18 script/paper 3.Rmd
@@
 ---
-title: "Untitled"
-author: "Jiayi Du"
-date: "2022/3/17"
-output: pdf_document
+title: "Canadian Family"
+subtitle: "My subtitle if needed"
+author: 
+  - Alicia Yang
+  - [Another author]
+  - []
+thanks: "Code and data are available at: https://github.com/dujiayi1/Factors-that-affect-happiness."
+date: "`r format(Sys.time(), '%d %B %Y')`"
+abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+output:
+  bookdown::pdf_document2
+toc: FALSE
+bibliography: references.bib
 ---
@@
 ```{r}
-gss<-read.csv("gss.csv",header=TRUE)
+gss<- read_csv(here::here(".Factors-that-affect-happiness/input/gss_family.csv"))
 gss<-gss%>%select(age,feelings_life,sex,marital_status,education,hh_size,average_hours_worked,income_family,income_respondent)

### 2022-03-18 script/gss_cleaning.R

@@ -1,0 +1,377 @@
+#### Preamble ####
+# Purpose: The purpose of this code is to clean-up the 2017 GSS data obtained 
+# from the U of T library. That data is available to U of T students, but it needs 
+# to be put into a tidy format before it can be analysed. This code does that.
+# The main issue is that the data are released with codes for variables, whereas,
+# we want the variable. e.g. sex is 1 or 2, but we want sex is female or male. (This
+# sounds trite in that case, but gets more difficult with more involved variables.)
+# So we create a dictionary type dataset that has the variable names and their 
+# possible values. In that we embed some R code that will do a replacement. We 
+# then apply that dataset to the raw dataset. Finally we do all the usual cleaning.
+# to the dataset. You will end up with a dataset called gss.csv.
+# Authors: Alicia Yang ,[] , []
+# Contact: aliciam.yang@utoronto.ca, [], []
+# Date: 20 March 2020
+# Pre-reqs: You need to have downloaded the data from the library. To do that: 
+  ## 1. Go to: http://www.chass.utoronto.ca/
+  ## 2. Data centre --> UofT users or http://dc.chass.utoronto.ca/myaccess.html
+  ## 3. Click SDA @ CHASS, should redirect to sign in. Sign in.
+  ## 4. Continue in English (you're welcome to use the French, but we probably can't
+  ## help you too much).
+  ## 5. Crtl F GSS, click
+  ## 6. Click "Data" on the one you want. We used 2017, but you may want a different 
+  ## wave. In particular the General Social Survey on social identity (cycle 27), 
+  ## 2013 has some variables on voter participation if you're into that sort of 
+  ## thing. You're welcome to pick any year but this code applies to 2017.
+  ## 7. Click download
+  ## 8. Select CSV data file, data definitions for STATA (gross, but stick with it for now).
+  ## 9. Can select all variables by clicking button next to green colored "All". Then continue.
+  ## 10. Create the files, download and save
+# Check: 
+  ## You WILL need to change the raw data name. Search for .csv - line 41
+  ## You may need to adjust the filepaths depending on your system. Search for: read_
+
+
[…]

### 2022-03-18 script/gss_cleaning.R
fix1

@@ -38,9 +38,9 @@ library(tidyverse)
 
 # Load the data dictionary and the raw data and correct the variable names
 raw_data <- read_csv("Factors-that-affect-happiness/input/gss.csv")
-dict <- read_lines("Factors-that-affect-happiness/input/data/gss_dict.txt", skip = 18) # skip is because of preamble content
+dict <- read_lines("Factors-that-affect-happiness/input/gss_dict.txt", skip = 18) # skip is because of preamble content
 # Now we need the labels because these are the actual responses that we need
-labels_raw <- read_file("Factors-that-affect-happiness/input/data/gss_labels.txt")
+labels_raw <- read_file("Factors-that-affect-happiness/input/gss_labels.txt")
 
 
 #### Set-up the dictionary ####

### 2022-03-18 output/paper3.Rmd
Add files via upload

---
title: "Untitled"
author: "Jiayi Du"
date: "2022/3/17"
output: pdf_document
---

```{r, include=FALSE, echo=FALSE}
library(janitor)
library(tidyverse)

# Load the data dictionary and the raw data and correct the variable names
raw_data <- read_csv("gss.csv")
dict <- read_lines("gss_dict.txt", skip = 18) # skip is because of preamble content
# Now we need the labels because these are the actual responses that we need
labels_raw <- read_file("gss_labels.txt")

#### Set-up the dictionary ####
# What we want is a variable name and a variable definition
variable_descriptions <- as_tibble(dict) %>% 
  filter(value!="}") %>% 
  mutate(value = str_replace(value, ".+%[0-9].*f[ ]{2,}", "")) %>% 
  mutate(value = str_remove_all(value, "\"")) %>% 
  rename(variable_description = value) %>% 
  bind_cols(tibble(variable_name = colnames(raw_data)[-1]))

# Now we want a variable name and the possible values
labels_raw_tibble <- as_tibble(str_split(labels_raw, ";")[[1]]) %>% 
  filter(row_number()!=1) %>% 
  mutate(value = str_remove(value, "\nlabel define ")) %>% 
  mutate(value = str_replace(value, "[ ]{2,}", "XXX")) %>% 
  mutate(splits = str_split(value, "XXX")) %>% 
  rowwise() %>% 
  mutate(variable_name = splits[1], cases = splits[2]) %>% 
  mutate(cases = str_replace_all(cases, "\n [ ]{2,}", "")) %>%
  select(variable_name, cases) %>% 
  drop_na()

# Now we have the variable name and the different options e.g. age and 0-9, 10-19, etc.
labels_raw_tibble <- labels_raw_tibble %>% 
  mutate(splits = str_split(cases, "[ ]{0,}\"[ ]{0,}"))

# The function sets up the regex (I know, I know, but eh: https://xkcd.com/208/)
add_cw_text <- function(x, y){
  if(!is.na(as.numeric(x))){
    x_new <- paste0(y, "==", x,"~")
  }
  else{
    x_new <- paste0("\"",x,"\",")
  }
  return(x_new)
}

# The function will be in the row, but it'll get the job done
cw_statements <- labels_raw_tibble %>% 
  rowwise() %>% 
  mutate(splits_with_cw_text = list(modify(splits, add_cw_text, y = variable_name))) %>% 
  mutate(cw_statement = paste(splits_with_cw_text, collapse = "")) %>% 
  mutate(cw_statement = paste0("case_when(", cw_statement,"TRUE~\"NA\")")) %>% 
  mutate(cw_statement = str_replace(cw_statement, ",\"\",",",")) %>% 
  select(variable_name, cw_statement)
# So for every variable we now have a case_when() statement that will convert 
# from the number to the actual response.

# Just do some finally cleanup of the regex.
cw_statements <- 
  cw_statements %>% 
  mutate(variable_name = str_remove_all(variable_name, "\\r")) %>% 
  mutate(cw_statement = str_remove_all(cw_statement, "\\r"))

#### Apply that dictionary to the raw data ####
# Pull out a bunch of variables and then apply the case when statement for the categorical variables
gss <- raw_data %>% 
  select(CASEID, 
         agedc, 
         achd_1c, 
         achdmpl, 
         totchdc, 
         acu0c,
         agema1c,
         achb1c,
         rsh_131a,
         arretwk,
         slm_01, 
         sex, 
         brthcan, 
         brthfcan,
         brthmcan,
         brthmacr,
         brthprvc,
         yrarri,
         prv, 
         region, 
         luc_rst, 
         marstat, 
         amb_01, 
         vismin, 
         alndimmg,
         bpr_16, 
         bpr_19,
         ehg3_01b, 
         odr_10, 
         livarr12, 
         dwelc, 
         hsdsizec,
         brthpcan,
         brtpprvc, 
         visminpr,
         rsh_125a, 
         eop_200,
         uhw_16gr,
         lmam_01, 
         acmpryr,
         srh_110,
         srh_115,
         religflg, 
         rlr_110,
         lanhome, 
         lan_01,
         famincg2, 
         ttlincg2, 
         noc1610, 
         cc_20_1,
         cc_30_1,
         ccmoc1c,
         cor_031,
         cor_041,
         cu0rnkc,
         pr_cl,
         chh0014c,
         nochricc,
         grndpa,
         gparliv,
         evermar,
         ma0_220,
         nmarevrc,
         ree_02,
         rsh_131b,
         rto_101,
         rto_110,
         rto_120,
         rtw_300,
         sts_410,
         csp_105,
         csp_110a,
         csp_110b,
         csp_110c,
         csp_110d,
         csp_160,
         fi_110) %>% 
  mutate_at(vars(agedc:fi_110), .funs = funs(ifelse(.>=96, NA, .))) %>% 
  mutate_at(.vars = vars(sex:fi_110),
            .funs = funs(eval(parse(text = cw_statements %>%
                                      filter(variable_name==deparse(substitute(.))) %>%
                                      select(cw_statement) %>%
                                      pull()))))

# Fix the names
gss <- gss %>% 
  clean_names() %>% 
  rename(age = agedc,
         age_first_child = achd_1c,
         age_youngest_child_under_6 = achdmpl,
         total_children = totchdc,
         age_start_relationship = acu0c,
         age_at_first_marriage = agema1c,
         age_at_first_birth = achb1c,
         distance_between_houses = rsh_131a,
         age_youngest_child_returned_work = arretwk,
         feelings_life = slm_01,
         sex = sex,
         place_birth_canada = brthcan,
         place_birth_father = brthfcan,
         place_birth_mother = brthmcan,
         place_birth_macro_region = brthmacr,
         place_birth_province = brthprvc,
         year_arrived_canada = yrarri,
         province = prv,
         region = region,
         pop_center = luc_rst,
         marital_status = marstat,
         aboriginal = amb_01,
         vis_minority = vismin,
         age_immigration = alndimmg,
         landed_immigrant = bpr_16,
         citizenship_status = bpr_19,
         education = ehg3_01b,
         own_rent = odr_10,
         living_arrangement = livarr12,
         hh_type = dwelc,
         hh_size = hsdsizec,
         partner_birth_country = brthpcan,
         partner_birth_province = brtpprvc,
         partner_vis_minority = visminpr,
         partner_sex = rsh_125a,
         partner_education = eop_200,
         average_hours_worked = uhw_16gr,
         worked_last_week = lmam_01,
         partner_main_activity = acmpryr,
         self_rated_health = srh_110,
         self_rated_mental_health = srh_115,
         religion_has_affiliation = religflg,
         regilion_importance = rlr_110,
         language_home = lanhome,
         language_knowledge = lan_01,
         income_family = famincg2,
         income_respondent = ttlincg2,
         occupation = noc1610,
         childcare_regular = cc_20_1,
         childcare_type = cc_30_1,
         childcare_monthly_cost = ccmoc1c,
         ever_fathered_child = cor_031,
         ever_given_birth = cor_041,
         number_of_current_union = cu0rnkc,
         lives_with_partner = pr_cl,
         children_in_household = chh0014c,
         number_total_children_intention = nochricc,
         has_grandchildren = grndpa,
         grandparents_still_living = gparliv,
         ever_married = evermar,
         current_marriage_is_first = ma0_220,
         number_marriages = nmarevrc,
         religion_participation = ree_02,
         partner_location_residence = rsh_131b,
         full_part_time_work = rto_101,
         time_off_work_birth = rto_110,
         reason_no_time_off_birth = rto_120,
         returned_same_job = rtw_300,
         satisfied_time_children = sts_410,
         provide_or_receive_fin_supp = csp_105,
         fin_supp_child_supp = csp_110a,
         fin_supp_child_exp = csp_110b,
         fin_supp_lump = csp_110c,
         fin_supp_other = csp_110d,
         fin_supp_agreement = csp_160,
         future_children_intention = fi_110)

#### Clean up ####
gss <- gss %>% 
  mutate_at(vars(age:future_children_intention), 
            .funs = funs(ifelse(.=="Valid skip"|.=="Refusal"|.=="Not stated", "NA", .)))

gss <- gss %>% 
  mutate(is_male = ifelse(sex=="Male", 1, 0))

gss <- gss %>% 
  mutate_at(vars(fin_supp_child_supp:fin_supp_other), .funs = funs(case_when(
    .=="Yes"~1,
    .=="No"~0,
    .=="NA"~as.numeric(NA)
  )))

main_act <- raw_data %>% 
  mutate(main_activity = case_when(
    mpl_105a=="Yes"~ "Working at a paid job/business",
    mpl_105b=="Yes" ~ "Looking for paid work",
    mpl_105c=="Yes" ~ "Going to school",
    mpl_105d=="Yes" ~ "Caring for children",
    mpl_105e=="Yes" ~ "Household work", 
    mpl_105i=="Yes" ~ "Other", 
    TRUE~ "NA")) %>% 
  select(main_activity) %>% 
  pull()

age_diff <- raw_data %>% 
  select(marstat, aprcu0c, adfgrma0) %>% 
  mutate_at(.vars = vars(aprcu0c:adfgrma0),
            .funs = funs(eval(parse(text = cw_statements %>%
                                      filter(variable_name==deparse(substitute(.))) %>%
                                      select(cw_statement) %>%
                                      pull())))) %>% 
  mutate(age_diff = ifelse(marstat=="Living common-law", aprcu0c, adfgrma0)) %>% 
  mutate_at(vars(age_diff), .funs = funs(ifelse(.=="Valid skip"|.=="Refusal"|.=="Not stated", "NA", .))) %>% 
  select(age_diff) %>% 
  pull()

gss <- gss %>% mutate(main_activity = main_act, age_diff = age_diff)

# Change some from strings into numbers
gss <- gss %>% 
  rowwise() %>% 
  mutate(hh_size = str_remove(string = hh_size, pattern = "\\ .*")) %>% 
  mutate(hh_size = case_when(
    hh_size=="One" ~ 1,
    hh_size=="Two" ~ 2,
    hh_size=="Three" ~ 3,
    hh_size=="Four" ~ 4,
    hh_size=="Five" ~ 5,
    hh_size=="Six" ~ 6
  ))

gss <- gss %>% 
  rowwise() %>% 
  mutate(self_rated_health = str_remove(string = self_rated_health, pattern = "\\ .*")) %>% 
  mutate(self_rated_health = case_when(
    self_rated_health=="Poor" ~ 1,
    self_rated_health=="Fair" ~ 2,
    self_rated_health=="Good" ~ 3,
    self_rated_health=="Very good" ~ 4,
    self_rated_health=="Excellent" ~ 5,
    self_rated_health=="Valid skip" ~ as.numeric(NA),
    self_rated_health=="Don't know" ~ as.numeric(NA),
    self_rated_health=="Refusal" ~ as.numeric(NA),
    self_rated_health=="Not stated" ~ as.numeric(NA)
  ))

gss <- gss %>% 
  rowwise() %>% 
  mutate(self_rated_mental_health = str_remove(string = self_rated_mental_health, pattern = "\\ .*")) %>% 
  mutate(self_rated_mental_health = case_when(
    self_rated_mental_health=="Poor" ~ 1,
    self_rated_mental_health=="Fair" ~ 2,
    self_rated_mental_health=="Good" ~ 3,
    self_rated_mental_health=="Very good" ~ 4,
    self_rated_mental_health=="Excellent" ~ 5,
    self_rated_mental_health=="Valid skip" ~ as.numeric(NA),
    self_rated_mental_health=="Don't know" ~ as.numeric(NA),
    self_rated_mental_health=="Refusal" ~ as.numeric(NA),
    self_rated_mental_health=="Not stated" ~ as.numeric(NA)
  ))

gss <- gss %>% 
  rowwise() %>% 
  mutate(number_marriages = str_remove(string = number_marriages, pattern = "\\ .*")) %>% 
  mutate(number_marriages = case_when(
    number_marriages=="No" ~ 0,
    number_marriages=="One" ~ 1,
    number_marriages=="Two" ~ 2,
    number_marriages=="Three" ~ 3,
    number_marriages=="Four" ~ 4
  ))

gss <- gss %>% 
  rowwise() %>% 
  mutate(number_total_children_known = ifelse(number_total_children_intention=="Don't know"|number_total_children_intention=="NA", 0, 1)) %>% 
  mutate(number_total_children_intention = str_remove(string = number_total_children_intention, pattern = "\\ .*")) %>% 
  mutate(number_total_children_intention = case_when(
    number_total_children_intention=="None" ~ 0,
    number_total_children_intention=="One" ~ 1,
    number_total_children_intention=="Two" ~ 2,
    number_total_children_intention=="Three" ~ 3,
    number_total_children_intention=="Four" ~ 4,
    number_total_children_intention=="Don't" ~ as.numeric(NA)
  ))

write_csv(gss, "gss_family.csv")
```

# Introduction
Different aspects of the Canadian society has entered a relatively stable stage in the past few decades, such as its economy and politics. However, it doesn’t mean that the Canadians haven’t been experiencing changes that drastically affect their lifestyles. Factors including social policies and technology advancements have greatly shift the Canadians’ ideology, values, and one of the most common change is their attitude towards marriage. Surveys have shown that more than half of the Canadians see no reasons in getting legally married. They tend to form common low relationships or simply stay single, because from their perspectives, it seemed like marriages are more likely to end up in a mess than happiness.

The General Social Survey(GSS) conducted a survey to Canadians on the topic of Family in 2017. By utilizing the data collected from the survey, this paper aims to explore the different possible factors that affect the happiness of single and married people, such as age, sex, marital status, personal income, average working hours and so on. Then we demonstrate possible concerns of Canadian families… In addition, we will give suggestions to improve their life quality.

In this paper, we are only interested in the respondents who are single or married. We focused on these (number) variables: age, personal income, family income, sex, average working hours and education.
Variable “age” indicates the age of the survey respondents. We restrict the age group to respondents between 18 and 80 years old. Variable “feelings_life” indicates how the respondents generally feel about their life from a scale of 0 to 10. Variable “income_respondent” provides the personal income of the respondents from all possible sources. Variable "income_family" represents the total income of the family. Variable "average_hours_worked" means the weekly working hours of the respondents. Variable "education" provides the education level of respondents. Variable "marital_status" indicates the marital status of respondents, and in this paper we mainly analyzed the respondents of "Married" and "Single, never married".

# Data

## Background

The survey we utilized in this paper comes from the General Social Survey(GSS) of Canada in 2017. The GSS program, founded in 1985, designed and conducted surveys targeting Canadians and focusing on different aspects of life each year.

The purpose of those surveys was to collect enough data to investigate potential social issues faced by Canadians, seek for approaches to address these issues, and improve their life quality and personal wellness. This paper selected the GSS in 2017, which focused on the topic of evolution of Families. This questionnaire has a total of 20602 samples and 460 variables. Its target respondents are the 
people who live in Canada who are older than 15.

## Methodology

The survey questions were tested by Statistics Canada's Questionnaire Design Resource Center beforehand. Screened participants from two cities were selected to complete the questionnaire. Base on the feedback of these participants, questions were improved to enhance the effectiveness of the survey. The sampling frame of this survey was created by the Census and Statistics Canada's dwelling frame, The respondents were accessed by landline and cellular telephone numbers, and only one member from each of the selected households 
was asked to fill the questionnaire. Stratified sampling was used to select the respondents. The Canadian population was divided into 27 strata based on the provinces and census metropolitan areas.

Minimum number of random samples were picked from each of the strata to reduce the bias. Invitation letters were sent to the sampled households prior to the official survey to increase the response rate.

```{r include=FALSE}
gss<-read.csv("gss_family.csv",header=TRUE)
gss<-gss%>%select(age,feelings_life,sex,marital_status,education,average_hours_worked,income_family,income_respondent)
```

```{r, echo=FALSE}
gss<-gss%>%na.omit(gss)
gss<-gss%>%filter(marital_status=="Married"|marital_status=="Single, never married")%>%filter(average_hours_worked!="Don't know")
glimpse(gss)
```

```{r}
library(ggplot2)
ggplot(gss,aes(x=feelings_life,fill=income_family))+geom_histogram(position = position_dodge(0.75),binwidth = 1)+facet_grid(.~marital_status)

```

```{r}
ggplot(gss,aes(x=feelings_life,fill=average_hours_worked))+geom_histogram(position = position_dodge(0.75),binwidth = 1)+facet_grid(.~marital_status)

```

```{r}
ggplot(gss,aes(x=feelings_life,fill=education))+geom_histogram(position = position_dodge(0.75),binwidth = 1)+facet_grid(.~marital_status)
```

```{r}
ggplot(aes(x = age, fill = marital_status), data = gss) +geom_histogram(binwidth = 0.2)+facet_wrap(~feelings_life)
ggplot(aes(x = feelings_life, fill = sex), data = gss) +geom_bar(position = "dodge")+facet_wrap(~marital_status)
```

# Discussion

##Strengths

The response rate of GSS in 2017 is approximately 52.4%, which is a pretty high number. To make sure that the samples were representative of the target population, the survey data were applied by a weighing factor so that the outcome of the survey was more accurate. Confidentiality rules prevented the respondents’ personal information to be disclosed without permission.

##Weaknesses

Some questions which appeared to be quite sensitive to many respondents resulted in high non-response rates. For instance, respondents were generally unwilling to provide information about their incomes. As a result, the information 
about income was acquired by the tax returns filed by the respondents from the previous year, and the variable “income” was set to a categorical variable.

However, this made the survey data collected much vaguer and less likely to reflect the true statistics of income.
Some bias were associated with the GSS data. For instance, not all target population was covered by the sampling method. The group of households without telephones were not included in the sampled population, which potentially increased the bias of the survey data. Non-response bias was resulted from the group of sampled populations who did not respond to the survey.

### 2022-03-18 output/paper3.Rmd
data+result

@@
 ---
-title: "Untitled"
-author: "Jiayi Du"
-date: "2022/3/17"
-output: pdf_document
+title: "Canadian Family..."
+subtitle: "My subtitle if needed"
+author: 
+  - Alicia Yang
+  - [Another author]
+  - []
+thanks: "Code and data are available at: https://github.com/dujiayi1/Factors-that-affect-happiness."
+date: "`r format(Sys.time(), '%d %B %Y')`"
+abstract: "First sentence.
+Second sentence.
+Third sentence.
+Fourth sentence....Then we demonstrate possible concerns of Canadian families… In addition, we will give suggestions to improve their life quality."
+output:
+  bookdown::pdf_document2
+toc: FALSE
+bibliography: references.bib
 ---
@@
 ```{r, include=FALSE, echo=FALSE}
+#Setup libraries
 library(janitor)
 library(tidyverse)
-
-# Load the data dictionary and the raw data and correct the variable names
-raw_data <- read_csv("gss.csv")
-dict <- read_lines("gss_dict.txt", skip = 18) # skip is because of preamble content
-# Now we need the labels because these are the actual responses that we need
-labels_raw <- read_file("gss_labels.txt")
-
-#### Set-up the dictionary ####
-# What we want is a variable name and a variable definition
-variable_descriptions <- as_tibble(dict) %>% 
-  filter(value!="}") %>% 
-  mutate(value = str_replace(value, ".+%[0-9].*f[ ]{2,}", "")) %>% 
-  mutate(value = str_remove_all(value, "\"")) %>% 
-  rename(variable_description = value) %>% 
-  bind_cols(tibble(variable_name = colnames(raw_data)[-1]))
-
-# Now we want a variable name and the possible values
-labels_raw_tibble <- as_tibble(str_split(labels_raw, ";")[[1]]) %>% 
-  filter(row_number()!=1) %>% 
-  mutate(value = str_remove(value, "\nlabel define ")) %>% 
-  mutate(value = str_replace(value, "[ ]{2,}", "XXX")) %>% 
-  mutate(splits = str_split(value, "XXX")) %>% 
-  rowwise() %>% 
-  mutate(variable_name = splits[1], cases = splits[2]) %>% 
-  mutate(cases = str_replace_all(cases, "\n [ ]{2,}", "")) %>%
-  select(variable_name, cases) %>% 
-  drop_na()
-
-# Now we have the variable name and the different options e.g. age and 0-9, 10-19, etc.
-labels_raw_tibble <- labels_raw_tibble %>% 
-  mutate(splits = str_split(cases, "[ ]{0,}\"[ ]{0,}"))
-
-# The function sets up the regex (I know, I know, but eh: https://xkcd.com/208/)
-add_cw_text <- function(x, y){
-  if(!is.na(as.numeric(x))){
-    x_new <- paste0(y, "==", x,"~")
-  }
-  else{
-    x_new <- paste0("\"",x,"\",")
-  }
-  return(x_new)
-}
-
-# The function will be in the row, but it'll get the job done
-cw_statements <- labels_raw_tibble %>% 
-  rowwise() %>% 
-  mutate(splits_with_cw_text = list(modify(splits, add_cw_text, y = variable_name))) %>% 
-  mutate(cw_statement = paste(splits_with_cw_text, collapse = "")) %>% 
-  mutate(cw_statement = paste0("case_when(", cw_statement,"TRUE~\"NA\")")) %>% 
-  mutate(cw_statement = str_replace(cw_statement, ",\"\",",",")) %>% 
-  select(variable_name, cw_statement)
-# So for every variable we now have a case_when() statement that will convert 
-# from the number to the actual response.
-
-# Just do some finally cleanup of the regex.
-cw_statements <- 
-  cw_statements %>% 
-  mutate(variable_name = str_remove_all(variable_name, "\\r")) %>% 
-  mutate(cw_statement = str_remove_all(cw_statement, "\\r"))
-
-#### Apply that dictionary to the raw data ####
-# Pull out a bunch of variables and then apply the case when statement for the categorical variables
-gss <- raw_data %>% 
-  select(CASEID, 
-         agedc, 
-         achd_1c, 
-         achdmpl, 
-         totchdc, 
-         acu0c,
-         agema1c,
-         achb1c,
-         rsh_131a,
-         arretwk,
-         slm_01, 
-         sex, 
-         brthcan, 
-         brthfcan,
-         brthmcan,
-         brthmacr,
-         brthprvc,
-         yrarri,
-         prv, 
-         region, 
-         luc_rst, 
-         marstat, 
-         amb_01, 
-         vismin, 
-         alndimmg,
-         bpr_16, 
-         bpr_19,
-         ehg3_01b, 
-         odr_10, 
-         livarr12, 
-         dwelc, 
-         hsdsizec,
-         brthpcan,
-         brtpprvc, 
-         visminpr,
-         rsh_125a, 
-         eop_200,
-         uhw_16gr,
-         lmam_01, 
-         acmpryr,
-         srh_110,
-         srh_115,
-         religflg, 
-         rlr_110,
-         lanhome, 
-         lan_01,
-         famincg2, 
-         ttlincg2, 
-         noc1610, 
-         cc_20_1,
-         cc_30_1,
-         ccmoc1c,
-         cor_031,
-         cor_041,
-         cu0rnkc,
-         pr_cl,
-         chh0014c,
-         nochricc,
-         grndpa,
-         gparliv,
-         evermar,
-         ma0_220,
-         nmarevrc,
-         ree_02,
-         rsh_131b,
-         rto_101,
-         rto_110,
-         rto_120,
-         rtw_300,
-         sts_410,
-         csp_105,
-         csp_110a,
-         csp_110b,
-         csp_110c,
-         csp_110d,
-         csp_160,
-         fi_110) %>% 
-  mutate_at(vars(agedc:fi_110), .funs = funs(ifelse(.>=96, NA, .))) %>% 
-  mutate_at(.vars = vars(sex:fi_110),
-            .funs = funs(eval(parse(text = cw_statements %>%
-                                      filter(variable_name==deparse(substitute(.))) %>%
-                                      select(cw_statement) %>%
-                                      pull()))))
-
-# Fix the names
-gss <- gss %>% 
-  clean_names() %>% 
-  rename(age = agedc,
-         age_first_child = achd_1c,
-         age_youngest_child_under_6 = achdmpl,
-         total_children = totchdc,
-         age_start_relationship = acu0c,
-         age_at_first_marriage = agema1c,
-         age_at_first_birth = achb1c,
-         distance_between_houses = rsh_131a,
-         age_youngest_child_returned_work = arretwk,
-         feelings_life = slm_01,
-         sex = sex,
-         place_birth_canada = brthcan,
-         place_birth_father = brthfcan,
-         place_birth_mother = brthmcan,
-         place_birth_macro_region = brthmacr,
-         place_birth_province = brthprvc,
-         year_arrived_canada = yrarri,
-         province = prv,
-         region = region,
-         pop_center = luc_rst,
-         marital_status = marstat,
-         aboriginal = amb_01,
-         vis_minority = vismin,
-         age_immigration = alndimmg,
-         landed_immigrant = bpr_16,
-         citizenship_status = bpr_19,
-         education = ehg3_01b,
-         own_rent = odr_10,
-         living_arrangement = livarr12,
-         hh_type = dwelc,
-         hh_size = hsdsizec,
-         partner_birth_country = brthpcan,
-         partner_birth_province = brtpprvc,
-         partner_vis_minority = visminpr,
-         partner_sex = rsh_125a,
-         partner_education = eop_200,
-         average_hours_worked = uhw_16gr,
-         worked_last_week = lmam_01,
-         partner_main_activity = acmpryr,
-         self_rated_health = srh_110,
-         self_rated_mental_health = srh_115,
-         religion_has_affiliation = religflg,
-         regilion_importance = rlr_110,
-         language_home = lanhome,
-         language_knowledge = lan_01,
-         income_family = famincg2,
-         income_respondent = ttlincg2,
-         occupation = noc1610,
-         childcare_regular = cc_20_1,
-         childcare_type = cc_30_1,
-         childcare_monthly_cost = ccmoc1c,
-         ever_fathered_child = cor_031,
-         ever_given_birth = cor_041,
-         number_of_current_union = cu0rnkc,
-         lives_with_partner = pr_cl,
-         children_in_household = chh0014c,
-         number_total_children_intention = nochricc,
-         has_grandchildren = grndpa,
-         grandparents_still_living = gparliv,
-         ever_married = evermar,
-         current_marriage_is_first = ma0_220,
-         number_marriages = nmarevrc,
-         religion_participation = ree_02,
-         partner_location_residence = rsh_131b,
-         full_part_time_work = rto_101,
-         time_off_work_birth = rto_110,
-         reason_no_time_off_birth = rto_120,
-         returned_same_job = rtw_300,
-         satisfied_time_children = sts_410,
-         provide_or_receive_fin_supp = csp_105,
-         fin_supp_child_supp = csp_110a,
-         fin_supp_child_exp = csp_110b,
-         fin_supp_lump = csp_110c,
-         fin_supp_other = csp_110d,
-         fin_supp_agreement = csp_160,
-         future_children_intention = fi_110)
-
-#### Clean up ####
-gss <- gss %>% 
-  mutate_at(vars(age:future_children_intention), 
-            .funs = funs(ifelse(.=="Valid skip"|.=="Refusal"|.=="Not stated", "NA", .)))
-
-gss <- gss %>% 
-  mutate(is_male = ifelse(sex=="Male", 1, 0))
-
-gss <- gss %>% 
-  mutate_at(vars(fin_supp_child_supp:fin_supp_other), .funs = funs(case_when(
-    .=="Yes"~1,
-    .=="No"~0,
-    .=="NA"~as.numeric(NA)
-  )))
-
-main_act <- raw_data %>% 
-  mutate(main_activity = case_when(
-    mpl_105a=="Yes"~ "Working at a paid job/business",
-    mpl_105b=="Yes" ~ "Looking for paid work",
-    mpl_105c=="Yes" ~ "Going to school",
-    mpl_105d=="Yes" ~ "Caring for children",
-    mpl_105e=="Yes" ~ "Household work", 
-    mpl_105i=="Yes" ~ "Other", 
-    TRUE~ "NA")) %>% 
-  select(main_activity) %>% 
-  pull()
-
-age_diff <- raw_data %>% 
-  select(marstat, aprcu0c, adfgrma0) %>% 
-  mutate_at(.vars = vars(aprcu0c:adfgrma0),
-            .funs = funs(eval(parse(text = cw_statements %>%
-                                      filter(variable_name==deparse(substitute(.))) %>%
-                                      select(cw_statement) %>%
-                                      pull())))) %>% 
-  mutate(age_diff = ifelse(marstat=="Living common-law", aprcu0c, adfgrma0)) %>% 
-  mutate_at(vars(age_diff), .funs = funs(ifelse(.=="Valid skip"|.=="Refusal"|.=="Not stated", "NA", .))) %>% 
-  select(age_diff) %>% 
-  pull()
-
-gss <- gss %>% mutate(main_activity = main_act, age_diff = age_diff)
-
-# Change some from strings into numbers
-gss <- gss %>% 
-  rowwise() %>% 
-  mutate(hh_size = str_remove(string = hh_size, pattern = "\\ .*")) %>% 
-  mutate(hh_size = case_when(
-    hh_size=="One" ~ 1,
-    hh_size=="Two" ~ 2,
-    hh_size=="Three" ~ 3,
-    hh_size=="Four" ~ 4,
-    hh_size=="Five" ~ 5,
-    hh_size=="Six" ~ 6
-  ))
-
-gss <- gss %>% 
-  rowwise() %>% 
-  mutate(self_rated_health = str_remove(string = self_rated_health, pattern = "\\ .*")) %>% 
-  mutate(self_rated_health = case_when(
-    self_rated_health=="Poor" ~ 1,
-    self_rated_health=="Fair" ~ 2,
-    self_rated_health=="Good" ~ 3,
-    self_rated_health=="Very good" ~ 4,
-    self_rated_health=="Excellent" ~ 5,
-    self_rated_health=="Valid skip" ~ as.numeric(NA),
-    self_rated_health=="Don't know" ~ as.numeric(NA),
-    self_rated_health=="Refusal" ~ as.numeric(NA),
-    self_rated_health=="Not stated" ~ as.numeric(NA)
-  ))
-
-gss <- gss %>% 
-  rowwise() %>% 
-  mutate(self_rated_mental_health = str_remove(string = self_rated_mental_health, pattern = "\\ .*")) %>% 
-  mutate(self_rated_mental_health = case_when(
-    self_rated_mental_health=="Poor" ~ 1,
-    self_rated_mental_health=="Fair" ~ 2,
-    self_rated_mental_health=="Good" ~ 3,
-    self_rated_mental_health=="Very good" ~ 4,
-    self_rated_mental_health=="Excellent" ~ 5,
-    self_rated_mental_health=="Valid skip" ~ as.numeric(NA),
-    self_rated_mental_health=="Don't know" ~ as.numeric(NA),
-    self_rated_mental_health=="Refusal" ~ as.numeric(NA),
-    self_rated_mental_health=="Not stated" ~ as.numeric(NA)
-  ))
-
-gss <- gss %>% 
-  rowwise() %>% 
-  mutate(number_marriages = str_remove(string = number_marriages, pattern = "\\ .*")) %>% 
-  mutate(number_marriages = case_when(
-    number_marriages=="No" ~ 0,
-    number_marriages=="One" ~ 1,
-    number_marriages=="Two" ~ 2,
-    number_marriages=="Three" ~ 3,
-    number_marriages=="Four" ~ 4
-  ))
-
-gss <- gss %>% 
-  rowwise() %>% 
-  mutate(number_total_children_known = ifelse(number_total_children_intention=="Don't know"|number_total_children_intention=="NA", 0, 1)) %>% 
-  mutate(number_total_children_intention = str_remove(string = number_total_children_intention, pattern = "\\ .*")) %>% 
-  mutate(number_total_children_intention = case_when(
-    number_total_children_intention=="None" ~ 0,
-    number_total_children_intention=="One" ~ 1,
-    number_total_children_intention=="Two" ~ 2,
-    number_total_children_intention=="Three" ~ 3,
-    number_total_children_intention=="Four" ~ 4,
-    number_total_children_intention=="Don't" ~ as.numeric(NA)
-  ))
-
-write_csv(gss, "gss_family.csv")
 ```
@@
 The General Social Survey(GSS) conducted a survey to Canadians on the topic of Family in 2017.
-By utilizing the data collected from the survey, this paper aims to explore the different possible factors that affect the happiness of single and married people, such as age, sex, marital status, personal income, average working hours and so on.
-Then we demonstrate possible concerns of Canadian families… In addition, we will give suggestions to improve their life quality.
-
-In this paper, we are only interested in the respondents who are single or married.
-We focused on these (number) variables: age, personal income, family income, sex, average working hours and education.
-Variable “age” indicates the age of the survey respondents.
-We restrict the age group to respondents between 18 and 80 years old.
-Variable “feelings_life” indicates how the respondents generally feel about their life from a scale of 0 to 10.
-Variable “income_respondent” provides the personal income of the respondents from all possible sources.
-Variable "income_family" represents the total income of the family.
-Variable "average_hours_worked" means the weekly working hours of the respondents.
-Variable "education" provides the education level of respondents.
-Variable "marital_status" indicates the marital status of respondents, and in this paper we mainly analyzed the respondents of "Married" and "Single, never married".
+By utilizing the data collected from the survey, we found that married people are actually more likely to be happier about their lives, which contradicts to how many people's perception about marriage and family.
+In order to understand how this controversy had formed, this paper aims to explore the different possible factors that affect the happiness of single and married people, such as age, sex, marital status, personal income, average working hours and so on.
+In Section \@ref(dataset-of-interest), ...
 
@@
 
-## Background
+```{r include=FALSE}
+# Load GSS family data
+gss<- read_csv(here::here("input/gss_family.csv"))
+gss<-gss%>%select(age,feelings_life,sex,marital_status, average_hours_worked,income_family,income_respondent) %>%
+  filter(marital_status == "Married" | marital_status == "Single, never married")
+```
 
+## Dataset of interest
 The survey we utilized in this paper comes from the General Social Survey(GSS) of Canada in 2017.
 The GSS program, founded in 1985, designed and conducted surveys targeting Canadians and focusing on different aspects of life each year.
-
 The purpose of those surveys was to collect enough data to investigate potential social issues faced by Canadians, seek for approaches to address these issues, and improve their life quality and personal wellness.
@@
 This questionnaire has a total of 20602 samples and 460 variables.
-Its target respondents are the
-people who live in Canada who are older than 15.
+Its target respondents are the people who live in Canada who are older than 15.
+
+This paper focused on investigating 6 of these variables: age, family income, sex, average working hours, and feelings about life.
+Variable “age” indicates the age of the survey respondents.
+Variable “feelings_life” indicates how the respondents generally feel about their life from a scale of 0 to 10.
+Variable “income_respondent” provides the personal income of the respondents from all possible sources.
+Variable "income_family" represents the total income of the family from all possible sources.
+Variable “sex” indicates indicates the sexuality of the respondents.
+Variable "average_hours_worked" means the weekly working hours of the respondents.
+Variable “marital_status” gives information on whether the respondents are single, living common-law, married, separated, divorced, or widowed; in this paper, we are only interested in the respondents who are either single or married.
+
+R [@citeR], and R packages "tidyverse" [@citetidyverse], "janitor" [@citejanitor], "knitr" [@citeknitr], "dplyr" [@citedplyr], and "kableExtra" [@citekableExtra] are utilized to create an extract of the cleaned dataset (Table \@ref(tab:dataextract)).
+
+```{r dataextract, echo=FALSE, message=FALSE}
+# Set up libraries
+library(knitr)
+library(kableExtra)
+
+# Create a table
+gss_cleaned <- gss %>%
+  drop_na() %>%
+  slice(1:10) %>%
+  kable(
+    caption = "Extracting the first ten rows from the cleaned GSS Family survey dataset",
+col.names=c("Age", "Feelings about life", "Sex", "Marital status", "Average hours worked per week", "Family income", "Personal income"),
+linesep = "", digits = 1, booktabs=TRUE) %>%
+  kable_styling(latex_options = "HOLD_position", font_size = 9)
+gss_cleaned
+```
 
@@
 Base on the feedback of these participants, questions were improved to enhance the effectiveness of the survey.
-The sampling frame of this survey was created by the Census and Statistics Canada's dwelling frame, The respondents were accessed by landline and cellular telephone numbers, and only one member from each of the selected households
-was asked to fill the questionnaire. Stratified sampling was used to select the respondents. The Canadian population was divided into 27 strata based on the provinces and census metropolitan areas.
-
+The sampling frame of this survey was created by the Census and Statistics Canada's dwelling frame, The respondents were accessed by landline and cellular telephone numbers, and only one member from each of the selected households was asked to fill the questionnaire.
+Stratified sampling was used to select the respondents.
+The Canadian population was divided into 27 strata based on the provinces and census metropolitan areas.
 Minimum number of random samples were picked from each of the strata to reduce the bias.
@@
 
-```{r include=FALSE}
-gss<-read.csv("gss_family.csv",header=TRUE)
-gss<-gss%>%select(age,feelings_life,sex,marital_status,education,average_hours_worked,income_family,income_respondent)
+## Strengths
+
+The response rate of GSS in 2017 is approximately 52.4%, which is a pretty high number.
+To make sure that the samples were representative of the target population, the survey data were applied by a weighing factor so that the outcome of the survey was more accurate.
+Confidentiality rules prevented the respondents’ personal information to be disclosed without permission.
+
+## Weaknesses
+
+Some questions which appeared to be quite sensitive to many respondents resulted in high non-response rates.
+For instance, respondents were generally unwilling to provide information about their incomes.
+As a result, the information about income was acquired by the tax returns filed by the respondents from the previous year, and the variable “income” was set to a categorical variable.
+However, this made the survey data collected much vaguer and less likely to reflect the true statistics of income.
+Some bias were associated with the GSS data.
+For instance, not all target population was covered by the sampling method.
+The group of households without telephones were not included in the sampled population, which potentially increased the bias of the survey data.
+Non-response bias was resulted from the group of sampled populations who did not respond to the survey.
+
+# Results
+## Age
+```{r echo=FALSE, warning=FALSE, fig.cap="Comparing the rated feelings about life of different age groups between single and married people", fig.width=7, fig.height=3.2}
+age_rate <- gss %>%
+  select(age, feelings_life, marital_status) %>%
+  drop_na() %>%
+   mutate(age_group = case_when(
+    age < 30  ~ "15-30",
+    (age>=30 & age < 45) ~ "30-45",
+    (age>=45 & age < 60) ~ "45-60",
+    (age>=60 & age < 80) ~ "60-80",
+    (age>=80) ~ "greater than 80",
+  ))
+ggplot(aes(x = feelings_life, fill = age_group), data = age_rate)+geom_bar()+facet_wrap(~marital_status)+theme_minimal()+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "Age groups")
+
 ```
+
+Figure 1 demonstrates how different age groups of Canadians rate their lives and draws a comparison about this statistics between those who are married and those who’re single and never married.
+Considering the fact that the number of singled respondents decreased by age, it is unreasonable to simply compare between the two plots.
+By looking at the samples who are single, we can observe that a higher proportion of younger age groups rated their feelings about life high(between 7 and 10), while on the contrary, a higher proportion of older people rated their feelings about life low(between 3 and 6).
+For the samples of married people, it’s quite obvious that a much higher proportion of older people rated their feelings about life high(between 8 and 10).
 
@@
 gss<-gss%>%filter(marital_status=="Married"|marital_status=="Single, never married")%>%filter(average_hours_worked!="Don't know")
-glimpse(gss)
 ```
 
-```{r}
+```{r, echo = FALSE}
 library(ggplot2)
@@
 
-```{r}
+```{r, echo = FALSE}
 ggplot(gss,aes(x=feelings_life,fill=average_hours_worked))+geom_histogram(position = position_dodge(0.75),binwidth = 1)+facet_grid(.~marital_status)
@@
 
-```{r}
-ggplot(gss,aes(x=feelings_life,fill=education))+geom_histogram(position = position_dodge(0.75),binwidth = 1)+facet_grid(.~marital_status)
-```
-
-```{r}
-ggplot(aes(x = age, fill = marital_status), data = gss) +geom_histogram(binwidth = 0.2)+facet_wrap(~feelings_life)
-ggplot(aes(x = feelings_life, fill = sex), data = gss) +geom_bar(position = "dodge")+facet_wrap(~marital_status)
-```
-
 # Discussion
 
-##Strengths
+# Appendix
 
-The response rate of GSS in 2017 is approximately 52.4%, which is a pretty high number.
-To make sure that the samples were representative of the target population, the survey data were applied by a weighing factor so that the outcome of the survey was more accurate.
-Confidentiality rules prevented the respondents’ personal information to be disclosed without permission.
+\newpage
 
-##Weaknesses
-
-Some questions which appeared to be quite sensitive to many respondents resulted in high non-response rates.
-For instance, respondents were generally unwilling to provide information about their incomes.
-As a result, the information
-about income was acquired by the tax returns filed by the respondents from the previous year, and the variable “income” was set to a categorical variable.
-
-However, this made the survey data collected much vaguer and less likely to reflect the true statistics of income.
-Some bias were associated with the GSS data.
-For instance, not all target population was covered by the sampling method.
-The group of households without telephones were not included in the sampled population, which potentially increased the bias of the survey data.
-Non-response bias was resulted from the group of sampled populations who did not respond to the survey.
+# References

### 2022-03-18 script/gss_cleaning.R

@@ -12,6 +12,7 @@
 # Authors: Alicia Yang ,[] , []
 # Contact: aliciam.yang@utoronto.ca, [], []
 # Date: 20 March 2020
+# License: MIT
 # Pre-reqs: You need to have downloaded the data from the library. To do that: 
   ## 1. Go to: http://www.chass.utoronto.ca/
   ## 2. Data centre --> UofT users or http://dc.chass.utoronto.ca/myaccess.html

### 2022-03-18 output/paper3.Rmd
add bibs

@@
 Factors including social policies and technology advancements have greatly shift the Canadians’ ideology, values, and one of the most common change is their attitude towards marriage.
-Surveys have shown that more than half of the Canadians see no reasons in getting legally married.
+Surveys have shown that more than half of the Canadians see no reasons in getting legally married [@citeintro].
 They tend to form common low relationships or simply stay single, because from their perspectives, it seemed like marriages are more likely to end up in a mess than happiness.
 
-The General Social Survey(GSS) conducted a survey to Canadians on the topic of Family in 2017.
+The General Social Survey(GSS) conducted a survey to Canadians on the topic of Family in 2017 [@citeGSSdata].
 By utilizing the data collected from the survey, we found that married people are actually more likely to be happier about their lives, which contradicts to how many people's perception about marriage and family.
@@
 ## Dataset of interest
-The survey we utilized in this paper comes from the General Social Survey(GSS) of Canada in 2017.
+The survey we utilized in this paper comes from the General Social Survey(GSS) of Canada in 2017 [@citeGSSdata].
 The GSS program, founded in 1985, designed and conducted surveys targeting Canadians and focusing on different aspects of life each year.
 The purpose of those surveys was to collect enough data to investigate potential social issues faced by Canadians, seek for approaches to address these issues, and improve their life quality and personal wellness.
-This paper selected the GSS in 2017, which focused on the topic of evolution of Families.
+This paper selected the GSS which focused on the topic of evolution of Families.
 This questionnaire has a total of 20602 samples and 460 variables.
-Its target respondents are the people who live in Canada who are older than 15.
+Its target respondents are the people who live in Canada who are older than 15 [@citeGSSdata].
 
 This paper focused on investigating 6 of these variables: age, family income, sex, average working hours, and feelings about life.
-Variable “age” indicates the age of the survey respondents.
-Variable “feelings_life” indicates how the respondents generally feel about their life from a scale of 0 to 10.
-Variable “income_respondent” provides the personal income of the respondents from all possible sources.
-Variable "income_family" represents the total income of the family from all possible sources.
-Variable “sex” indicates indicates the sexuality of the respondents.
-Variable "average_hours_worked" means the weekly working hours of the respondents.
-Variable “marital_status” gives information on whether the respondents are single, living common-law, married, separated, divorced, or widowed; in this paper, we are only interested in the respondents who are either single or married.
-
 R [@citeR], and R packages "tidyverse" [@citetidyverse], "janitor" [@citejanitor], "knitr" [@citeknitr], "dplyr" [@citedplyr], and "kableExtra" [@citekableExtra] are utilized to create an extract of the cleaned dataset (Table \@ref(tab:dataextract)).
@@
     caption = "Extracting the first ten rows from the cleaned GSS Family survey dataset",
-col.names=c("Age", "Feelings about life", "Sex", "Marital status", "Average hours worked per week", "Family income", "Personal income"),
+col.names=c("Age", "Feelings about life", "Sex", "Marital status", "Average hours worked", "Family income", "Personal income"),
 linesep = "", digits = 1, booktabs=TRUE) %>%
@@
 ```
+
+Table \@ref(tab:dataextract) shows the first ten rows of the GSS Family dataset of interest .Variable “Age” indicates the age of the survey respondents.
+Variable “Feelings about life” indicates how the respondents generally feel about their life from a scale of 0 to 10.
+Variable “Sex” indicates indicates the sexuality of the respondents.
+Variable “Marital Status” gives information on whether the respondents are single, living common-law, married, separated, divorced, or widowed; in this paper, we are only interested in the respondents who are either single or married.
+Variable "Average hours worked" shows the weekly working hours of the respondents.
+Variable "Family income" represents the total income of the family from all possible sources.
+Variable “Personal income” provides the personal income of the respondents from all possible sources.
 
@@
 Minimum number of random samples were picked from each of the strata to reduce the bias.
-Invitation letters were sent to the sampled households prior to the official survey to increase the response rate.
+Invitation letters were sent to the sampled households prior to the official survey to increase the response rate [@citeGSSdata].
 
@@
 To make sure that the samples were representative of the target population, the survey data were applied by a weighing factor so that the outcome of the survey was more accurate.
-Confidentiality rules prevented the respondents’ personal information to be disclosed without permission.
+Confidentiality rules prevented the respondents’ personal information to be disclosed without permission [@citeGSSdata].
 
@@
 The group of households without telephones were not included in the sampled population, which potentially increased the bias of the survey data.
-Non-response bias was resulted from the group of sampled populations who did not respond to the survey.
+Non-response bias was resulted from the group of sampled populations who did not respond to the survey [@citeGSSdata].
 
@@
 For the samples of married people, it’s quite obvious that a much higher proportion of older people rated their feelings about life high(between 8 and 10).
+
+\newpage
+```{r echo=FALSE, warning=FALSE, fig.cap="Comparing the feelings about life between male and female for single and married people", fig.width=7, fig.height=3.2}
+sex_rate <- gss %>%
+  select(sex, feelings_life, marital_status) %>%
+  drop_na()
+ggplot(aes(x = feelings_life, fill = sex), data = sex_rate) +geom_bar(position = "dodge")+facet_wrap(~marital_status)+theme_minimal()+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "Sex")
+```
+
+Figure 2 compares the feelings about life between female and male when they are married or single and never married.
+For the group of singles, sexuality does not have a distinct influence on how they rate their feelings about life.
+Slightly more males than females rated their feelings for life between 7 and 8, but the number break even again between 9 and 10.
+However, when it comes to married people, it seemed like some females tend to give extreme high scores(score of 10) on their feelings about life.
+This implies that for most of the times, sexuality is not a big contributor to one’s satisfaction about his/her life when they are either single or married, yet it greatly increases some married females' happiness.
 

### 2022-03-19 output/paper3.Rmd
fix1

@@
 
-The General Social Survey(GSS) conducted a survey to Canadians on the topic of Family in 2017 [@citeGSSdata].
-By utilizing the data collected from the survey, we found that married people are actually more likely to be happier about their lives, which contradicts to how many people's perception about marriage and family.
-In order to understand how this controversy had formed, this paper aims to explore the different possible factors that affect the happiness of single and married people, such as age, sex, marital status, personal income, average working hours and so on.
-In Section \@ref(dataset-of-interest), ...
+The General Social Survey(GSS) conducted a survey on the topic of Canadian Families in 2017 [@citeGSSdata].
+By utilizing the data collected from the survey, we found that married couples are actually more likely to be happier about their lives than the singles, which contradicts to many people's perception about marriage and family.
+In order to understand how this controversy is formed, this paper aims to explore the different possible factors that affect the happiness of single and married people, such as age, sex, marital status, family income, average working hours and so on.
+The survey data is thoroughly discussed in the section of \@ref(data).
+In the sub-section \@ref(dataset-of-interest), we presented an overview of the original survey data, and explained our cleaned dataset that we'll for exploration.
+The methods used to collect the GSS data as well as the strengths and weaknesses associated with these methods are outlined in the sub-sections \@ref(methodology), \@ref(strengths), and \@ref(weaknesses).
+Section \@ref(results) presents a series of findings in relation to how the factors that we picked have impacts on
 
@@
 \newpage
+## Sexuality
 ```{r echo=FALSE, warning=FALSE, fig.cap="Comparing the feelings about life between male and female for single and married people", fig.width=7, fig.height=3.2}
@@
 Slightly more males than females rated their feelings for life between 7 and 8, but the number break even again between 9 and 10.
-However, when it comes to married people, it seemed like some females tend to give extreme high scores(score of 10) on their feelings about life.
+However, when it comes to married couples, it seemed like some females tend to give extreme high scores(score of 10) on their feelings about life.
 This implies that for most of the times, sexuality is not a big contributor to one’s satisfaction about his/her life when they are either single or married, yet it greatly increases some married females' happiness.

### 2022-03-19 output/paper3.Rmd
fix

@@
 gss<- read_csv(here::here("input/gss_family.csv"))
-gss<-gss%>%select(age,feelings_life,sex,marital_status, average_hours_worked,income_family,income_respondent) %>%
+gss <- gss %>% select(age,feelings_life,sex,marital_status, average_hours_worked,income_family,income_respondent, education) %>%
   filter(marital_status == "Married" | marital_status == "Single, never married")
@@
     caption = "Extracting the first ten rows from the cleaned GSS Family survey dataset",
-col.names=c("Age", "Feelings about life", "Sex", "Marital status", "Average hours worked", "Family income", "Personal income"),
+col.names=c("Age", "Feelings about life", "Sex", "Marital status", "Average hours worked", "Family income", "Personal income", "Education"),
 linesep = "", digits = 1, booktabs=TRUE) %>%

### 2022-03-19 output/paper3.Rmd
Add files via upload

@@
   - Alicia Yang
-  - [Another author]
-  - []
+  - [Jiayi Du]
+  - [Kaiyuan Yan]
 thanks: "Code and data are available at: https://github.com/dujiayi1/Factors-that-affect-happiness."
@@
 # Load GSS family data
-gss<- read_csv(here::here("input/gss_family.csv"))
+gss<- read_csv("gss_family.csv")
 gss <- gss %>% select(age,feelings_life,sex,marital_status, average_hours_worked,income_family,income_respondent, education) %>%
@@
 
-```{r, echo=FALSE}
+## Respodent income
+
+```{r include=FALSE}
 gss<-gss%>%na.omit(gss)
@@
 
-```{r, echo = FALSE}
-library(ggplot2)
-ggplot(gss,aes(x=feelings_life,fill=income_family))+geom_histogram(position = position_dodge(0.75),binwidth = 1)+facet_grid(.~marital_status)
+```{r, echo = FALSE, warning=FALSE, fig.cap="Comparing the feelings about life between different levels of income of respondents for single and married people", fig.width=9, fig.height=3.2}
+ggplot(gss,aes(x=feelings_life,fill=income_respondent))+geom_histogram(position = position_dodge(0.75),binwidth = 1)+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "respondent income")
 
@@
 
-```{r, echo = FALSE}
-ggplot(gss,aes(x=feelings_life,fill=average_hours_worked))+geom_histogram(position = position_dodge(0.75),binwidth = 1)+facet_grid(.~marital_status)
+Figure 3 indicates the effect on respondents' feelings about life by comparing the different income levels and it's divided by the marital status respectively.
+It is not hard to find that no matter they are married or single, their income level is high or low, their feelings about life are still eight points or above.
+In addition, interestingly, it seems that people with lower income levels are happier with their lives, especially among single and never married people.
+This implies that personal income actually may have a considerable impact on the people's feeling about life.
+
+## Average working hours
+
+```{r, echo = FALSE,warning=FALSE, fig.cap="Comparing the feelings about life between different levels of working hours of respondents for single and married people", fig.width=8, fig.height=3.2}
+ggplot(gss,aes(x=feelings_life,fill=average_hours_worked))+geom_histogram(position = position_dodge(0.75),binwidth = 1)+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "working hours")
 
@@
 
+Figure 4 demonstrates the relationship between feelings about life and the weekly average working hours of respondents.
+It's not surprising to find that people with less working hours tend to have more points of feeling about life, which is much more apparent for married groups.
+It seems that people with 6-8 working hours every day may be happier about life.
+
+## Education
+
+```{r,echo=FALSE,warning=FALSE, fig.cap="Comparing the feelings about life between different levels of education of respondents for single and married people", fig.width=10, fig.height=3.2}
+ggplot(gss,aes(x=feelings_life,fill=education))+geom_histogram(position = position_dodge(0.75),binwidth = 1)+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "education level")
+
+```
+Figure 5 shows that, as for married people, education level has some effect on feelings about life while it has little influence on single people.
+For married people, it seems that higher education level may lead to more points of feeling about life.
+Most of the married respondents with bachelor's degree or college certificate have more than 8 points of feeling about life, which indicates that married people with a relatively high education level may feel much happier about life.
+
 # Discussion
+
+## Personal income
+
+From our perspective, it might be tempting to assume that people with higher incomes are likely to be happier because they have more purchasing power and higher consumption levels, making it easier for them to buy things than ordinary people who have to take a long time to save up for.
+However, in this paper, it’s quite surprising to find that people who are married with high income tend to be less happy than people who earn less.
+After consideration and discussion, the possible reasons are as follows:
+
+On one hand, people who have been married have more pressure about their family, not only the family daily expenses, but also a large proportion of possible expenses from raising children.
+For them, a large part of the high salary earned by hard work every day is for family expenses, and there may even be a feeling of being on the run all the time, which makes them feel less happy with life.
+
+On the other hand, people who are single right now spend most of their salary on themselves, no matter they go out to eat, drink or buy things for themselves.
+There is less pressure, so they are more likely to feel satisfied and happy about life.
+
+## Working hours
+
+It's not hard to understand that long working hours may have negative effect on the people's feeling about life, since working for a long time with high intensity will definitely have a great impact on people both physically and psychologically.
+
+However, it seems more obvious that long working hours have more impact on married people than single people.
+In our opinion, since married people may have more pressure from their family, it's quite normal for them to feel more relaxed if they have less working hours.
+They may be able to take a break and enjoy their life better.
+
+Although working hours are often positively correlated with income, as we have previously analyzed, higher income does not necessarily mean increased happiness with life, so working longer hours does not necessarily mean greater satisfaction and happiness with life.
+
+## Education
+
+In fact, most of the time, education has a certain relationship with the factor we discussed before, the working hours and personal income .
+It seems that nowadays, people with higher degrees tend to be able to find higher-paying jobs, but higher-paying jobs often mean longer working hours.
+
+However, from the discussion above, we find that more personal income and working hours don't mean greater happiness.
+Thus, we consider the other reasons for education level leading to higher level of happiness.
+The biggest reason We can accept is that for the highly educated married people, they may have wider horizons and richer thoughts.
+Especially when faced with setbacks in life and feeling depressed, they can quickly deal with them and have a more positive attitude towards life.
+Moreover, in the family they are able to understand each other and accommodate with each other.
+As a result, family life is often more harmonious.
+
+## Weakness and limitations
+
+Our results are more directly reflected by images, and then we make subjective summaries and think about the reasons behind them.
+We do not specifically point out the influence of factors that affect feelings about life.
+With more study, we can use more statistical knowledge to conduct modeling and analysis to obtain the specific influence of different factors, so as to exclude the deviation caused by some subjective factors.
+
+Moreover, due to the individual differences among different people, working long hours does not necessarily mean high income, and high income does not necessarily mean working long hours.
+In addition, highly educated people do not necessarily have a high-paying job.
+All these may cause bias to our results.
+
+Besides, in fact, everyone's feelings towards life will be affected by many aspects.
+No matter personal thoughts or mentality, may have much influence on a person's feelings towards life.
+However, these are not reflected by a simple survey and table, which may produce deviations in our results.
 

### 2022-03-19 output/paper3.Rmd
merge

--- 2022-03-19 output/paper3.Rmd
@@
 To make sure that the samples were representative of the target population, the survey data were applied by a weighing factor so that the outcome of the survey was more accurate.
-Confidentiality rules prevented the respondents’ personal information to be disclosed without permission [@citeGSSdata].
+Issues associated with ethics were reduced due to the confidentiality rules of Statistics Canada and prevented the respondents’ personal information to be disclosed without permission [@citeGSSdata].
 
@@
 By looking at the samples who are single, we can observe that a higher proportion of younger age groups rated their feelings about life high(between 7 and 10), while on the contrary, a higher proportion of older people rated their feelings about life low(between 3 and 6).
-For the samples of married people, it’s quite obvious that a much higher proportion of older people rated their feelings about life high(between 8 and 10).
+For the samples of married people, it’s quite obvious that a much higher proportion of older people rated their feelings about life with high scores between 8 and 10.
 

### 2022-03-19 output/paper3.Rmd
intro, absrtact and discussion

@@
 date: "`r format(Sys.time(), '%d %B %Y')`"
-abstract: "First sentence.
-Second sentence.
-Third sentence.
-Fourth sentence....Then we demonstrate possible concerns of Canadian families… In addition, we will give suggestions to improve their life quality."
+abstract: "In recent years Canadian society has shown diverse attitude towards the idea of forming a family.
+To investigate on the reason behind this controversy, this paper conducted the research on the factors which may have an impact on single and married people’s feelings about life based on the General Social Survey(GSS).
+After screening and comparison, we found that the factors that may affect people’s feelings about life in the survey include age, respondent income, sex, average working hours, and education level.
+By observing the result, we found that single people of younger age with less income and less working hours feel happier about life, while married peole of older age with less income and less working hours and higher education level feel more satisfied with their life.
+Moreover, we analyzed the reason for these factors causing effect and discussed the possible bias in the research and the solutions to it."
 output:
@@
 However, it doesn’t mean that the Canadians haven’t been experiencing changes that drastically affect their lifestyles.
-Factors including social policies and technology advancements have greatly shift the Canadians’ ideology, values, and one of the most common change is their attitude towards marriage.
+Factors including social policies and technology advancements have greatly shift the Canadians’ ideology, values, and one of the most common change is their attitude towards marriage and forming family.
 Surveys have shown that more than half of the Canadians see no reasons in getting legally married [@citeintro].
@@
 The methods used to collect the GSS data as well as the strengths and weaknesses associated with these methods are outlined in the sub-sections \@ref(methodology), \@ref(strengths), and \@ref(weaknesses).
-Section \@ref(results) presents a series of findings in relation to how the factors that we picked have impacts on
+Section \@ref(results) presents a series of findings in relation to how the different aspects we picked have impacts on single and married people’s feelings about life.
+These aspects include age, sexuality, average hours worked, respondent income, and education level.
+In section \@ref(discussion), a discussion is made to elaborate on the implications of the findings we've got from the survey data.
+Furthermore, we talked about the possible reasons that lead to the the effect of these factors on single and married people's feelings about life.
+
+A supplementary survey is provided in the Appendix in section \@ref(appendix) that incorporate the main focus of this paper and the general social survey.
+It is designed to obtain more information to enhance the quality of the survey data and to pursue further investigation on this topic.
 
@@
 # Load GSS family data
-gss<- read_csv("gss_family.csv")
-gss <- gss %>% select(age,feelings_life,sex,marital_status, average_hours_worked,income_family,income_respondent, education) %>%
+gss<- read_csv(here::here("input/gss_family.csv"))
+gss <- gss %>% select(feelings_life,marital_status, age, sex, income_respondent, average_hours_worked, education) %>%
+  mutate(age = case_when(
+    age < 30  ~ "15-30",
+    (age>=30 & age < 45) ~ "30-45",
+    (age>=45 & age < 60) ~ "45-60",
+    (age>=60 & age < 80) ~ "60-80",
+    (age>=80) ~ "greater than 80",
+  )) %>%
   filter(marital_status == "Married" | marital_status == "Single, never married")
@@
 
-This paper focused on investigating 6 of these variables: age, family income, sex, average working hours, and feelings about life.
+This paper focused on investigating 6 of these variables: age, sex, respondent's income, average working hours, and feelings about life.
 R [@citeR], and R packages "tidyverse" [@citetidyverse], "janitor" [@citejanitor], "knitr" [@citeknitr], "dplyr" [@citedplyr], and "kableExtra" [@citekableExtra] are utilized to create an extract of the cleaned dataset (Table \@ref(tab:dataextract)).
@@
     caption = "Extracting the first ten rows from the cleaned GSS Family survey dataset",
-col.names=c("Age", "Feelings about life", "Sex", "Marital status", "Average hours worked", "Family income", "Personal income", "Education"),
+col.names=c("Feelings about life", "Marital status", "Age", "Sex", "Average hours worked", "Respondent income", "Education"),
 linesep = "", digits = 1, booktabs=TRUE) %>%
-  kable_styling(latex_options = "HOLD_position", font_size = 9)
+  kable_styling(latex_options = "HOLD_position", font_size = 6)
 gss_cleaned
@@
 
-Table \@ref(tab:dataextract) shows the first ten rows of the GSS Family dataset of interest .Variable “Age” indicates the age of the survey respondents.
+Table \@ref(tab:dataextract) shows the first ten rows of the GSS Family dataset of interest .Variable “Age” indicates the age group of the survey respondents.
 Variable “Feelings about life” indicates how the respondents generally feel about their life from a scale of 0 to 10.
@@
 Variable "Average hours worked" shows the weekly working hours of the respondents.
-Variable "Family income" represents the total income of the family from all possible sources.
-Variable “Personal income” provides the personal income of the respondents from all possible sources.
+Variable “Personal income” indicates the personal income of the respondents from all possible sources.
 
@@
 
-## Respodent income
+## Respondent income
 
@@
 
-## Average working hours
+## Average weekly working hours
 
@@
 # Discussion
+
+## Ageing and Family life
+
+In section \@ref(age), we’ve discussed that older people with families tend to feel better about their lives compared to younger age groups, and at the same time, younger people that have not yet form families also tend to feel better about their lives when comparing to single elderly people.
+One possible explanation for this particular result is difference between young and old people in terms of their ideology, health conditions, and social status.
+Family would be a strong support for the elders who have high risks to experience illnesses, social isolations, and financial crisis.
+The younger generations, on the other hand, who are more capable of overcoming the crisis faced by the elders, often value the importance of having personal space and feeling controlled of their own lives more.
+Family has both advantages and drawbacks from looking at these two perspectives, so it’s not surprised that Canadians have such diverse attitudes towards family.
 
@@
 
-## Weakness and limitations
+## Weaknesses and limitations
 
@@
 
+\newpage
 # Appendix

### 2022-03-19 output/paper3.Rmd
fix layout

@@
 By utilizing the data collected from the survey, we found that married couples are actually more likely to be happier about their lives than the singles, which contradicts to many people's perception about marriage and family.
-In order to understand how this controversy is formed, this paper aims to explore the different possible factors that affect the happiness of single and married people, such as age, sex, marital status, family income, average working hours and so on.
+In order to understand how this controversy is formed, this paper aims to explore the different possible factors that affect the happiness of single and married people, such as age, sex, marital status, personal income, average working hours and so on.
 The survey data is thoroughly discussed in the section of \@ref(data).
@@
     (age>=80) ~ "greater than 80",
+  )) %>%
+  mutate(education = case_when(
+    education == "Bachelor's degree (e.g. B.A., B.Sc., LL.B.)" ~ "Bachelor's degree",
+    education == "University certificate, diploma or degree above the bach..." ~ "University certificate/diploma",
+    education =="College, CEGEP or other non-university certificate or di..."  ~ "Non-university certificate/diplomas",
+    education == "Trade certificate or diploma" ~ "Trade certificate/diploma",
+    education =="High school diploma or a high school equivalency certificate"  ~ "High school diploma/certificate",
+    education == "Less than high school diploma or its equivalent" ~ "Less than high school diploma"
   )) %>%
@@
 linesep = "", digits = 1, booktabs=TRUE) %>%
-  kable_styling(latex_options = "HOLD_position", font_size = 6)
+  kable_styling(latex_options = "HOLD_position", font_size = 5.7)
 gss_cleaned
@@
 ## Age
-```{r echo=FALSE, warning=FALSE, fig.cap="Comparing the rated feelings about life of different age groups between single and married people", fig.width=7, fig.height=3.2}
+```{r figure1, echo=FALSE, warning=FALSE, fig.cap="Comparing the rated feelings about life of different age groups between single and married people", fig.width=7, fig.height=3.5}
 age_rate <- gss %>%
@@
 
-Figure 1 demonstrates how different age groups of Canadians rate their lives and draws a comparison about this statistics between those who are married and those who’re single and never married.
+Figure \@ref(fig:figure1) demonstrates how different age groups of Canadians rate their lives and draws a comparison about this statistics between those who are married and those who’re single and never married.
 Considering the fact that the number of singled respondents decreased by age, it is unreasonable to simply compare between the two plots.
@@
 ## Sexuality
-```{r echo=FALSE, warning=FALSE, fig.cap="Comparing the feelings about life between male and female for single and married people", fig.width=7, fig.height=3.2}
+```{r figure2, echo=FALSE, warning=FALSE, fig.cap="Comparing the feelings about life between male and female for single and married people", fig.width=7, fig.height=3.5}
 sex_rate <- gss %>%
@@
   drop_na()
-ggplot(aes(x = feelings_life, fill = sex), data = sex_rate) +geom_bar(position = "dodge")+facet_wrap(~marital_status)+theme_minimal()+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "Sex")
+ggplot(aes(x = feelings_life, fill = sex), data = sex_rate) +geom_bar(position = "dodge", binwidth = 1)+facet_wrap(~marital_status)+theme_minimal()+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "Sex")
 ```
 
-Figure 2 compares the feelings about life between female and male when they are married or single and never married.
+Figure \@ref(fig:figure2) compares the feelings about life between female and male when they are married or single and never married.
 For the group of singles, sexuality does not have a distinct influence on how they rate their feelings about life.
@@
 
+Figure \@ref(fig:figure3) indicates the effect on respondents' feelings about life by comparing the different income levels and it's divided by the marital status respectively.
+It is not hard to find that no matter they are married or single, their income level is high or low, their feelings about life are still eight points or above.
+In addition, interestingly, it seems that people with lower income levels are happier with their lives, especially among single and never married people.
+This implies that personal income actually may have a considerable impact on the people's feeling about life.
+
+\newpage
 ```{r include=FALSE}
@@
 
-```{r, echo = FALSE, warning=FALSE, fig.cap="Comparing the feelings about life between different levels of income of respondents for single and married people", fig.width=9, fig.height=3.2}
-ggplot(gss,aes(x=feelings_life,fill=income_respondent))+geom_histogram(position = position_dodge(0.75),binwidth = 1)+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "respondent income")
+```{r figure3, echo = FALSE, warning=FALSE, fig.cap="Comparing the feelings about life between different levels of income of respondents for single and married people", fig.width=9, fig.height= 4.5}
+ggplot(gss,aes(x=feelings_life,fill=income_respondent))+geom_bar(position = "dodge",binwidth = 1)+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "respondent income")+theme_minimal()
+```
+
+## Average weekly working hours
+
+Figure \@ref(fig:figure4) demonstrates the relationship between feelings about life and the weekly average working hours of respondents.
+It's not surprising to find that people with less working hours tend to have more points of feeling about life, which is much more apparent for married groups.
+It seems that people with 6-8 working hours every day may be happier about life.
+
+\newpage
+```{r figure4, echo = FALSE,warning=FALSE, fig.cap="Comparing the feelings about life between different levels of working hours of respondents for single and married people", fig.width=8, fig.height=4.1}
+ggplot(gss,aes(x=feelings_life,fill=average_hours_worked))+geom_histogram(position = "dodge",binwidth = 1)+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "working hours")+theme_minimal()
 
@@
 
-Figure 3 indicates the effect on respondents' feelings about life by comparing the different income levels and it's divided by the marital status respectively.
-It is not hard to find that no matter they are married or single, their income level is high or low, their feelings about life are still eight points or above.
-In addition, interestingly, it seems that people with lower income levels are happier with their lives, especially among single and never married people.
-This implies that personal income actually may have a considerable impact on the people's feeling about life.
+## Education
 
-## Average weekly working hours
+Figure \@ref(fig:figure5) shows that, as for married people, education level has some effect on feelings about life while it has little influence on single people.
+For married people, it seems that higher education level may lead to more points of feeling about life.
+Most of the married respondents with bachelor's degree or college certificate have more than 8 points of feeling about life, which indicates that married people with a relatively high education level may feel much happier about life.
 
-```{r, echo = FALSE,warning=FALSE, fig.cap="Comparing the feelings about life between different levels of working hours of respondents for single and married people", fig.width=8, fig.height=3.2}
-ggplot(gss,aes(x=feelings_life,fill=average_hours_worked))+geom_histogram(position = position_dodge(0.75),binwidth = 1)+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "working hours")
+\newpage
+```{r figure5,echo=FALSE,warning=FALSE, fig.cap="Comparing the feelings about life between different levels of education of respondents for single and married people", fig.width=10, fig.height=4.8}
+ggplot(gss,aes(x=feelings_life,fill=education))+geom_histogram(position = "dodge",binwidth = 1)+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "education level")+theme_minimal()
 
 ```
-
-Figure 4 demonstrates the relationship between feelings about life and the weekly average working hours of respondents.
-It's not surprising to find that people with less working hours tend to have more points of feeling about life, which is much more apparent for married groups.
-It seems that people with 6-8 working hours every day may be happier about life.
-
-## Education
-
-```{r,echo=FALSE,warning=FALSE, fig.cap="Comparing the feelings about life between different levels of education of respondents for single and married people", fig.width=10, fig.height=3.2}
-ggplot(gss,aes(x=feelings_life,fill=education))+geom_histogram(position = position_dodge(0.75),binwidth = 1)+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "education level")
-
-```
-Figure 5 shows that, as for married people, education level has some effect on feelings about life while it has little influence on single people.
-For married people, it seems that higher education level may lead to more points of feeling about life.
-Most of the married respondents with bachelor's degree or college certificate have more than 8 points of feeling about life, which indicates that married people with a relatively high education level may feel much happier about life.
 
@@
 One possible explanation for this particular result is difference between young and old people in terms of their ideology, health conditions, and social status.
-Family would be a strong support for the elders who have high risks to experience illnesses, social isolations, and financial crisis.
+Family would be a strong support for the elders who have high risks to experience illnesses, social isolation, and financial crisis.
 The younger generations, on the other hand, who are more capable of overcoming the crisis faced by the elders, often value the importance of having personal space and feeling controlled of their own lives more.

### 2022-03-19 output/paper3.Rmd
fix result

@@
 
-Table \@ref(tab:dataextract) shows the first ten rows of the GSS Family dataset of interest .Variable “Age” indicates the age group of the survey respondents.
+Table \@ref(tab:dataextract) shows the first ten rows of the GSS Family dataset of interest .Variable “Age” indicates the age group of the survey respondents; it is used as a categorical variable in this paper for the purpose of comparing respondents by groups.
 Variable “Feelings about life” indicates how the respondents generally feel about their life from a scale of 0 to 10.
@@
 Variable “Marital Status” gives information on whether the respondents are single, living common-law, married, separated, divorced, or widowed; in this paper, we are only interested in the respondents who are either single or married.
-Variable "Average hours worked" shows the weekly working hours of the respondents.
-Variable “Personal income” indicates the personal income of the respondents from all possible sources.
+Variable "Average hours worked" shows the range of weekly working hours of the respondents.
+Variable “Personal income” indicates the range of personal income of the respondents from all possible sources each year.
 
@@
   ))
-ggplot(aes(x = feelings_life, fill = age_group), data = age_rate)+geom_bar()+facet_wrap(~marital_status)+theme_minimal()+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "Age groups")
+ggplot(aes(x = feelings_life, fill = age_group), data = age_rate)+geom_bar(position = "dodge")+facet_wrap(~marital_status)+theme_minimal()+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "Age groups")
 
@@
 Figure \@ref(fig:figure1) demonstrates how different age groups of Canadians rate their lives and draws a comparison about this statistics between those who are married and those who’re single and never married.
-Considering the fact that the number of singled respondents decreased by age, it is unreasonable to simply compare between the two plots.
+Considering the fact that the number of singled respondents decrease by age, it is unreasonable to simply compare between the two plots.
 By looking at the samples who are single, we can observe that a higher proportion of younger age groups rated their feelings about life high(between 7 and 10), while on the contrary, a higher proportion of older people rated their feelings about life low(between 3 and 6).
@@
 Slightly more males than females rated their feelings for life between 7 and 8, but the number break even again between 9 and 10.
-However, when it comes to married couples, it seemed like some females tend to give extreme high scores(score of 10) on their feelings about life.
+However, when it comes to married couples, it seems like some females tend to give extreme high scores(score of 10) on their feelings about life.
 This implies that for most of the times, sexuality is not a big contributor to one’s satisfaction about his/her life when they are either single or married, yet it greatly increases some married females' happiness.
@@
 Figure \@ref(fig:figure3) indicates the effect on respondents' feelings about life by comparing the different income levels and it's divided by the marital status respectively.
-It is not hard to find that no matter they are married or single, their income level is high or low, their feelings about life are still eight points or above.
-In addition, interestingly, it seems that people with lower income levels are happier with their lives, especially among single and never married people.
-This implies that personal income actually may have a considerable impact on the people's feeling about life.
+It is not hard to observe that the group of singles generally has a lower income level than the group of married people.
+In addition, by comparing within single respondents, it is interesting to find out that people with lower income levels feel better about their lives than people with higher income levels.
+This implies that personal income actually may have a considerable impact on the single people's feeling about life.
+For the married people, it seems like income level has no significant correlation with their feelings about life; a considerable number of respondents who earn less than \$25000 a year rated their feelings at a score of 10, while some respondents that earn over \$100000 a year only rated their feelings at a score of 8.
 
@@
 ```{r figure3, echo = FALSE, warning=FALSE, fig.cap="Comparing the feelings about life between different levels of income of respondents for single and married people", fig.width=9, fig.height= 4.5}
-ggplot(gss,aes(x=feelings_life,fill=income_respondent))+geom_bar(position = "dodge",binwidth = 1)+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "respondent income")+theme_minimal()
+ggplot(gss,aes(x=feelings_life,fill=income_respondent))+geom_bar(position = "dodge")+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "respondent income")+theme_minimal()
 ```
@@
 
-Figure \@ref(fig:figure4) demonstrates the relationship between feelings about life and the weekly average working hours of respondents.
-It's not surprising to find that people with less working hours tend to have more points of feeling about life, which is much more apparent for married groups.
-It seems that people with 6-8 working hours every day may be happier about life.
+Figure \@ref(fig:figure4) demonstrates the relationship between feelings about life and the weekly average working hours of single and married respondents It's not surprised to find that the single respondents  with heavy working hours of 40 hours or more tend to give higher scores on feeling about life.
+On the other hand, for married people, It seems that people with approximately 30-40 working hours every week feel happier about their lives.
 
@@
 ```{r figure4, echo = FALSE,warning=FALSE, fig.cap="Comparing the feelings about life between different levels of working hours of respondents for single and married people", fig.width=8, fig.height=4.1}
-ggplot(gss,aes(x=feelings_life,fill=average_hours_worked))+geom_histogram(position = "dodge",binwidth = 1)+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "working hours")+theme_minimal()
+ggplot(gss,aes(x=feelings_life,fill=average_hours_worked))+geom_bar(position = "dodge",binwidth = 1)+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "working hours")+theme_minimal()
 
@@
 Figure \@ref(fig:figure5) shows that, as for married people, education level has some effect on feelings about life while it has little influence on single people.
-For married people, it seems that higher education level may lead to more points of feeling about life.
-Most of the married respondents with bachelor's degree or college certificate have more than 8 points of feeling about life, which indicates that married people with a relatively high education level may feel much happier about life.
+For married people, it seems that higher education level may lead to higher scores of feelings about life.
+Most of the married respondents with bachelor's degree or college certificate give higher scores of 8 or more on feeling about life, which indicates that married people with a relatively high education level may feel much happier about life.
 
@@
 ```{r figure5,echo=FALSE,warning=FALSE, fig.cap="Comparing the feelings about life between different levels of education of respondents for single and married people", fig.width=10, fig.height=4.8}
-ggplot(gss,aes(x=feelings_life,fill=education))+geom_histogram(position = "dodge",binwidth = 1)+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "education level")+theme_minimal()
+ggplot(gss,aes(x=feelings_life,fill=education))+geom_bar(position = "dodge")+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "education level")+theme_minimal()
 

### 2022-03-20 output/paper3.Rmd
discussion

@@
 ---
-title: "Canadian Family..."
+title: "Investigating the reason behind Candianss attitudes towards the idea of family"
 subtitle: "My subtitle if needed"
@@
   - Alicia Yang
-  - [Jiayi Du]
-  - [Kaiyuan Yan]
+  - Jiayi Du
+  - Kaiyuan Yan
 thanks: "Code and data are available at: https://github.com/dujiayi1/Factors-that-affect-happiness."
@@
 # Results
-## Age
+## Age vs Feelings about life
 ```{r figure1, echo=FALSE, warning=FALSE, fig.cap="Comparing the rated feelings about life of different age groups between single and married people", fig.width=7, fig.height=3.5}
@@
 
-\newpage
-## Sexuality
+## Gender vs Feelings about life
 ```{r figure2, echo=FALSE, warning=FALSE, fig.cap="Comparing the feelings about life between male and female for single and married people", fig.width=7, fig.height=3.5}
@@
 Slightly more males than females rated their feelings for life between 7 and 8, but the number break even again between 9 and 10.
-However, when it comes to married couples, it seems like some females tend to give extreme high scores(score of 10) on their feelings about life.
+However, when it comes to married couples, it seems like some females tend to give extremely high scores(score of 10) on their feelings about life.
 This implies that for most of the times, sexuality is not a big contributor to one’s satisfaction about his/her life when they are either single or married, yet it greatly increases some married females' happiness.
 
-## Respondent income
+## Respondent income vs Feelings about life
 
@@
 
-## Average weekly working hours
+## Average weekly working hours vs Feelings about life
 
 Figure \@ref(fig:figure4) demonstrates the relationship between feelings about life and the weekly average working hours of single and married respondents It's not surprised to find that the single respondents  with heavy working hours of 40 hours or more tend to give higher scores on feeling about life.
-On the other hand, for married people, It seems that people with approximately 30-40 working hours every week feel happier about their lives.
+On the other hand, for married people, It seems like people with approximately 30-40 working hours every week feel happier about their lives.
 
@@
 
-## Education
+## Education vs Feelings about life
 
@@
 
-In section \@ref(age), we’ve discussed that older people with families tend to feel better about their lives compared to younger age groups, and at the same time, younger people that have not yet form families also tend to feel better about their lives when comparing to single elderly people.
+In section \@ref(age-vs-feelings-about-life), we’ve discussed that older people with families tend to feel better about their lives compared to younger age groups, and at the same time, younger people that have not yet form families also tend to feel better about their lives when comparing to single elderly people.
 One possible explanation for this particular result is difference between young and old people in terms of their ideology, health conditions, and social status.
@@
 
+## Gender
+
+Gender does not play a big role in terms of affecting the single and married respondents' feelings about life.
+One possible implication drawn from this result is that the gender roles in the Canadian society is weakened and the gender gap is gradually diminishing, which is a good sign.
+Men and women were no longer expected perform their traditional responsibilities either as individuals or as family members.
+Instead, their responsibilities become similar.
+As a result, we don't see much difference between the happiness of men and women when they are either single or married as presented in section \@ref(gender-vs-feelings-about-life).
+Further investigations on the roles of gender in Canadian society in terms of their characters as individuals or family members is needed to support this conclusion.
+
 ## Personal income
@@
 From our perspective, it might be tempting to assume that people with higher incomes are likely to be happier because they have more purchasing power and higher consumption levels, making it easier for them to buy things than ordinary people who have to take a long time to save up for.
-However, in this paper, it’s quite surprising to find that people who are married with high income tend to be less happy than people who earn less.
+However, in this paper, it’s quite surprising to find that people who are married with extremely high income tend to be less happy than people who earn less.
 After consideration and discussion, the possible reasons are as follows:
@@
 
-It's not hard to understand that long working hours may have negative effect on the people's feeling about life, since working for a long time with high intensity will definitely have a great impact on people both physically and psychologically.
+It's not hard to understand that long working hours generally have negative effect on the people's feeling about life, since working for a long time with high intensity will definitely have a great impact on people both physically and psychologically.
 
-However, it seems more obvious that long working hours have more impact on married people than single people.
-In our opinion, since married people may have more pressure from their family, it's quite normal for them to feel more relaxed if they have less working hours.
-They may be able to take a break and enjoy their life better.
+However, it seems more obvious that long working hours have more negative impact on the married respondents, while many single respondents generally feel less repulsive to work for longer hours.
+In our opinion, since married people have more burdens and concerns regarding family issues, it's quite normal that they feel more pressured and feel the need to be more relaxed by having less working hours.
+With less working hours, they may be able to take a break and enjoy their life better.
+The single respondents, on the other side, are less concerned with this issue and thus generally don't mind working for longer period of times.
 
-Although working hours are often positively correlated with income, as we have previously analyzed, higher income does not necessarily mean increased happiness with life, so working longer hours does not necessarily mean greater satisfaction and happiness with life.
+Since working hours are often positively correlated with income, as we have previously analyzed, higher income does not necessarily mean increased happiness with life, and working longer hours does not necessarily indicate greater satisfaction as well.
 
@@
 
-In fact, most of the time, education has a certain relationship with the factor we discussed before, the working hours and personal income .
+Most of the time, education has a certain relationship with the factor we discussed before, the working hours and personal income .
 It seems that nowadays, people with higher degrees tend to be able to find higher-paying jobs, but higher-paying jobs often mean longer working hours.
@@
 \newpage
-# Appendix
+# Appendix {-}
+# Supplementary Survey
+## Preamble
 

### 2022-03-20 script/gss_cleaning.R

@@ -9,7 +9,7 @@
 # possible values. In that we embed some R code that will do a replacement. We 
 # then apply that dataset to the raw dataset. Finally we do all the usual cleaning.
 # to the dataset. You will end up with a dataset called gss.csv.
-# Authors: Alicia Yang ,[] , []
+# Authors: Alicia Yang ,Jiayi Du , Kaiyuan Yan
 # Contact: aliciam.yang@utoronto.ca, [], []
 # Date: 20 March 2020
 # License: MIT

### 2022-03-20 output/paper3.Rmd
survey

@@
 ---
-title: "Investigating the reason behind Candianss attitudes towards the idea of family"
-subtitle: "My subtitle if needed"
+title: "Investigating the possible factors affecting Canadian Individuals and Families' feelings about life"
 author: 
@@
 Section \@ref(results) presents a series of findings in relation to how the different aspects we picked have impacts on single and married people’s feelings about life.
-These aspects include age, sexuality, average hours worked, respondent income, and education level.
+These aspects include age, gender, average hours worked, respondent income, and education level.
 In section \@ref(discussion), a discussion is made to elaborate on the implications of the findings we've got from the survey data.
@@
 Variable “Feelings about life” indicates how the respondents generally feel about their life from a scale of 0 to 10.
-Variable “Sex” indicates indicates the sexuality of the respondents.
+Variable “Sex” indicates indicates the gender of the respondents.
 Variable “Marital Status” gives information on whether the respondents are single, living common-law, married, separated, divorced, or widowed; in this paper, we are only interested in the respondents who are either single or married.
@@
 The Canadian population was divided into 27 strata based on the provinces and census metropolitan areas.
-Minimum number of random samples were picked from each of the strata to reduce the bias.
+Minimum number of random samples were picked from each of the strata to reduce the bias [@citetellingstorieswithdata].
 Invitation letters were sent to the sampled households prior to the official survey to increase the response rate [@citeGSSdata].
@@
 However, when it comes to married couples, it seems like some females tend to give extremely high scores(score of 10) on their feelings about life.
-This implies that for most of the times, sexuality is not a big contributor to one’s satisfaction about his/her life when they are either single or married, yet it greatly increases some married females' happiness.
+This implies that for most of the times, gender is not a big contributor to one’s satisfaction about his/her life when they are either single or married, yet it greatly increases some married females' happiness.
 
@@
 ## Preamble
+Canada is well known as one of the happiest countries on the planet.
+But what factor does Canadian think affect their feelings about life most?
+and how does it work?
+The purpose of this survey is to further investigate and elaborate on the main topic and discussions covered in this paper.
+We are interested in how these aspects: age, sex, average worked hours and personal income, affect Canadian's attitude towards family.
+
+By proceeding with this survey you understand that your responses will be used to better explore how these possible factors could affect Canadian individuals and families' feelings about life.
+Overall outcomes of this survey will be used to discuss our analysis result of the object,  but none of your responses will be used to identify you.
+Your responses will not be misused and will remain private.
+This survey is voluntary and if you decide to participate, you may skip any question(s) and withdraw at anytime.
+
+## Link to the Survey
+Below is the QR Code and the link of the survey.
+
+```{r echo=FALSE, fig.cap="QR Code of the survey", out.width = '40%', fig.align="center"}
+knitr::include_graphics("../input/QRCode.jpeg")
+```
+Survey Link:
+
+https://docs.google.com/forms/d/e/1FAIpQLSfCSQHzb-R61uIOLdmOCcdocRX9Ws-Z2NssHhxpLTRltjDItQ/viewform?usp=pp_url
+
+## Questions
+```{r echo = FALSE, out.width = '70%', fig.align="center"}
+knitr::include_graphics("../input/survey1.png")
+knitr::include_graphics("../input/survey2.png")
+```
+
+## End Page
+Thanks you for completing this survey.
+We really appreciate your time.
+If you have any questions, please feel free to contact us at aliciam.yang@mail.utoronto.ca, bruce.yan@mail.utoronto.ca, or claire.du@mail.utoronto.ca.
 

### 2022-03-20 script/gss_cleaning.R

@@ -10,7 +10,7 @@
 # then apply that dataset to the raw dataset. Finally we do all the usual cleaning.
 # to the dataset. You will end up with a dataset called gss.csv.
 # Authors: Alicia Yang ,Jiayi Du , Kaiyuan Yan
-# Contact: aliciam.yang@utoronto.ca, [], []
+# Contact: aliciam.yang@utoronto.ca, claire.du@mail.utoronto.ca, bruce.yan@mail.utoronto.ca
 # Date: 20 March 2020
 # License: MIT
 # Pre-reqs: You need to have downloaded the data from the library. To do that: 

### 2022-03-20 output/paper3.Rmd
fix survey and others

@@
 ---
-title: "Investigating the possible factors affecting Canadian Individuals and Families' feelings about life"
+title: "Investigating the possible aspects affecting Canadian Individuals and Families' feelings about life"
 author: 
@@
 In section \@ref(discussion), a discussion is made to elaborate on the implications of the findings we've got from the survey data.
-Furthermore, we talked about the possible reasons that lead to the the effect of these factors on single and married people's feelings about life.
+Furthermore, we talked about the possible reasons that lead to the effect of these factors on single and married people's feelings about life.
 
-A supplementary survey is provided in the Appendix in section \@ref(appendix) that incorporate the main focus of this paper and the general social survey.
+A supplementary survey is provided in the Appendix in section \@ref(supplementary-survey) that incorporate the main focus of this paper and the general social survey.
 It is designed to obtain more information to enhance the quality of the survey data and to pursue further investigation on this topic.
@@
 
+```{r figure0, echo=FALSE, warning=FALSE, fig.cap="Comparing the rated feelings about life between single and married people", fig.width=7, fig.height=3.5}
+ggplot(aes(x = feelings_life), data = gss)+geom_bar()+facet_wrap(~marital_status)+ylab("number of people")+xlab("feelings about life")+theme_minimal()
+```
+
+By looking at the distribution of survey data in Figure \@ref(fig:figure0) it seems like a much larger proportion(more than 70%) of married respondents have better feelings about life, giving scores between 8 to 10, while for the single respondents, a less percentage of them give high scores between 8 to 10 of how they feel about their life.
+This finding is contradicting to many Canadians' attitudes towards marriage and family, which is that it is unnecessary.
+Therefore, we will look into how different factors that we've selected cause the difference in attitude and feelings towards marriage, and what particular characteristics of each individuals make their single/married lives better.
+
+\newpage
 ## Methodology
@@
 ## Gender vs Feelings about life
+
+Figure \@ref(fig:figure2) compares the feelings about life between female and male when they are married or single and never married.
+For the group of singles, sexuality does not have a distinct influence on how they rate their feelings about life.
+Slightly more males than females rated their feelings for life between 7 and 8, but the number break even again between 9 and 10.
+However, when it comes to married couples, it seems like some females tend to give extremely high scores(score of 10) on their feelings about life.
+This implies that for most of the times, gender is not a big contributor to one’s satisfaction about his/her life when they are either single or married, yet it greatly increases some married females' happiness.
+
+\newpage
 ```{r figure2, echo=FALSE, warning=FALSE, fig.cap="Comparing the feelings about life between male and female for single and married people", fig.width=7, fig.height=3.5}
@@
 ```
-
-Figure \@ref(fig:figure2) compares the feelings about life between female and male when they are married or single and never married.
-For the group of singles, sexuality does not have a distinct influence on how they rate their feelings about life.
-Slightly more males than females rated their feelings for life between 7 and 8, but the number break even again between 9 and 10.
-However, when it comes to married couples, it seems like some females tend to give extremely high scores(score of 10) on their feelings about life.
-This implies that for most of the times, gender is not a big contributor to one’s satisfaction about his/her life when they are either single or married, yet it greatly increases some married females' happiness.
 
@@
 
-\newpage
 ```{r include=FALSE}
@@
 
+\newpage
 ## Average weekly working hours vs Feelings about life
@@
 
-\newpage
 ```{r figure4, echo = FALSE,warning=FALSE, fig.cap="Comparing the feelings about life between different levels of working hours of respondents for single and married people", fig.width=8, fig.height=4.1}
@@
 
+\newpage
 ## Education vs Feelings about life
@@
 
-\newpage
 ```{r figure5,echo=FALSE,warning=FALSE, fig.cap="Comparing the feelings about life between different levels of education of respondents for single and married people", fig.width=10, fig.height=4.8}
@@
 
+\newpage
 # Discussion
 
-## Ageing and Family life
+## Age
 
@@
 
+One possible bias in relation to this result is that as we seen in Figure \@ref(fig:figure5), education levels higher than Bachelor's degree is not an option in the survey, which means that respondents with higher degrees are not included in the discussion here.
+We will take account of this potential bias in the supplementary survey provided at the end of the paper.
+
 ## Weaknesses and limitations
@@
 knitr::include_graphics("../input/survey2.png")
+knitr::include_graphics("../input/survey3.png")
+knitr::include_graphics("../input/survey4.png")
+knitr::include_graphics("../input/survey5.png")
+knitr::include_graphics("../input/survey6.png")
+knitr::include_graphics("../input/survey7.png")
+knitr::include_graphics("../input/survey8.png")
+knitr::include_graphics("../input/survey9.png")
 ```

### 2022-03-21 output/paper3.Rmd
fix grammar

@@
 After screening and comparison, we found that the factors that may affect people’s feelings about life in the survey include age, respondent income, sex, average working hours, and education level.
-By observing the result, we found that single people of younger age with less income and less working hours feel happier about life, while married peole of older age with less income and less working hours and higher education level feel more satisfied with their life.
+By observing the result, we found that single people of younger age with less income and more working hours feel happier about life, while married peole of older age with less working hours and higher educational level feel more satisfied with their life.
 Moreover, we analyzed the reason for these factors causing effect and discussed the possible bias in the research and the solutions to it."
@@
 Different aspects of the Canadian society has entered a relatively stable stage in the past few decades, such as its economy and politics.
-However, it doesn’t mean that the Canadians haven’t been experiencing changes that drastically affect their lifestyles.
+However, it does not mean that the Canadians haven’t been experiencing changes that drastically affect their lifestyles.
 Factors including social policies and technology advancements have greatly shift the Canadians’ ideology, values, and one of the most common change is their attitude towards marriage and forming family.
@@
 A supplementary survey is provided in the Appendix in section \@ref(supplementary-survey) that incorporate the main focus of this paper and the general social survey.
-It is designed to obtain more information to enhance the quality of the survey data and to pursue further investigation on this topic.
+It is designed to obtain more information to enhance the quality of the survey data and to pursue further investigations on this topic.
 
@@
 In addition, by comparing within single respondents, it is interesting to find out that people with lower income levels feel better about their lives than people with higher income levels.
-This implies that personal income actually may have a considerable impact on the single people's feeling about life.
+This implies that personal income actually may have a considerable impact on the single people's happiness.
 For the married people, it seems like income level has no significant correlation with their feelings about life; a considerable number of respondents who earn less than \$25000 a year rated their feelings at a score of 10, while some respondents that earn over \$100000 a year only rated their feelings at a score of 8.
@@
 
-Figure \@ref(fig:figure5) shows that, as for married people, education level has some effect on feelings about life while it has little influence on single people.
+Figure \@ref(fig:figure5) shows that, education level has some effect on the married respondents' feelings about life while it has little influence on the single respondents.
 For married people, it seems that higher education level may lead to higher scores of feelings about life.
@@
 The younger generations, on the other hand, who are more capable of overcoming the crisis faced by the elders, often value the importance of having personal space and feeling controlled of their own lives more.
-Family has both advantages and drawbacks from looking at these two perspectives, so it’s not surprised that Canadians have such diverse attitudes towards family.
+Family has both advantages and drawbacks from looking at these two perspectives, so it’s not surprised that Canadians of different age groups have such diverse attitudes towards family.
 
@@
 From our perspective, it might be tempting to assume that people with higher incomes are likely to be happier because they have more purchasing power and higher consumption levels, making it easier for them to buy things than ordinary people who have to take a long time to save up for.
-However, in this paper, it’s quite surprising to find that people who are married with extremely high income tend to be less happy than people who earn less.
+However, in this paper, it’s quite surprising to find that married respondents with extremely high income tend to be less happy than people who earn less, and similarly, single respondents who earn lower wages also rate their feelings high.
 After consideration and discussion, the possible reasons are as follows:
 
-On one hand, people who have been married have more pressure about their family, not only the family daily expenses, but also a large proportion of possible expenses from raising children.
-For them, a large part of the high salary earned by hard work every day is for family expenses, and there may even be a feeling of being on the run all the time, which makes them feel less happy with life.
+People who have been married have more pressure about their family, not only the family daily expenses, but also a large proportion of possible expenses from raising children.
+For them, a large part of the high salary earned by hard work every day is for family expenses, and there may even be a feeling of being on the run all the time, which is not contributing positively to their feelings about life.
 
-On the other hand, people who are single right now spend most of their salary on themselves, no matter they go out to eat, drink or buy things for themselves.
+People who are single right now spend most of their salary on themselves, no matter they go out to eat, drink or buy things for themselves.
 There is less pressure, so they are more likely to feel satisfied and happy about life.

### 2022-03-21 output/paper3.Rmd
fix2

@@
 ---
-title: "Investigating the possible aspects affecting Canadian Individuals and Families' feelings about life"
+title: "Investigating the possible aspects affecting Canadian individuals and families' feelings about life"
 author: 

### 2022-03-21 output/paper3.Rmd
fix2

@@
 ---
-title: "Investigating the possible aspects affecting Canadian individuals and families' feelings about life"
+title: "Investigating the possible Factors affecting Canadian Individuals and Families' Feelings about Life"
 author: 

### 2022-03-21 output/paper3.Rmd
last commit

@@
 ```{r include=FALSE}
-# Load GSS family data
+# Load GSS family data and clean
 gss<- read_csv(here::here("input/gss_family.csv"))
@@
 
-# Create a table
+# Create a table of the cleaned gss data
 gss_cleaned <- gss %>%
@@
 ```{r figure0, echo=FALSE, warning=FALSE, fig.cap="Comparing the rated feelings about life between single and married people", fig.width=7, fig.height=3.5}
+# plot showing feelings about life between single and married people
 ggplot(aes(x = feelings_life), data = gss)+geom_bar()+facet_wrap(~marital_status)+ylab("number of people")+xlab("feelings about life")+theme_minimal()
@@
 ```{r figure1, echo=FALSE, warning=FALSE, fig.cap="Comparing the rated feelings about life of different age groups between single and married people", fig.width=7, fig.height=3.5}
+# plot showing relationship between age and feelings about life for single and married people
 age_rate <- gss %>%
@@
 ```{r figure2, echo=FALSE, warning=FALSE, fig.cap="Comparing the feelings about life between male and female for single and married people", fig.width=7, fig.height=3.5}
+# plot showing relationship between gender and feelings about life for single and married people
 sex_rate <- gss %>%
@@
 ```{r figure3, echo = FALSE, warning=FALSE, fig.cap="Comparing the feelings about life between different levels of income of respondents for single and married people", fig.width=9, fig.height= 4.5}
+# plot showing relationship between income and feelings about life for single and married people
 ggplot(gss,aes(x=feelings_life,fill=income_respondent))+geom_bar(position = "dodge")+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "respondent income")+theme_minimal()
@@
 ```{r figure4, echo = FALSE,warning=FALSE, fig.cap="Comparing the feelings about life between different levels of working hours of respondents for single and married people", fig.width=8, fig.height=4.1}
+# plot showing relationship between hours worked and feelings about life for single and married people
 ggplot(gss,aes(x=feelings_life,fill=average_hours_worked))+geom_bar(position = "dodge",binwidth = 1)+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "working hours")+theme_minimal()
@@
 ```{r figure5,echo=FALSE,warning=FALSE, fig.cap="Comparing the feelings about life between different levels of education of respondents for single and married people", fig.width=10, fig.height=4.8}
+# plot showing relationship between education and feelings about life for single and married people
 ggplot(gss,aes(x=feelings_life,fill=education))+geom_bar(position = "dodge")+facet_grid(.~marital_status)+ylab("number of people")+xlab("feelings about life")+scale_fill_discrete(name = "education level")+theme_minimal()
@@
 ```{r echo=FALSE, fig.cap="QR Code of the survey", out.width = '40%', fig.align="center"}
+#QR Code
 knitr::include_graphics("../input/QRCode.jpeg")
@@
 ```{r echo = FALSE, out.width = '70%', fig.align="center"}
+# survey questions
 knitr::include_graphics("../input/survey1.png")
